---
title             : "Título"
shorttitle        : "Título corto"

author: 
  - name          : "Marisa Casillas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "P.O. Box 310, 6500 AH Nijmegen, The Netherlands"
    email         : "Marisa.Casillas@mpi.nl"
  - name          : "Juan Méndez Girón"
    affiliation   : "2"
  - name          : "Melanie Soderstrom"
    affiliation   : "3"
  - name          : "Penelope Brown"
    affiliation   : "1"
  - name          : "Gilles Polian"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Max Planck Institute for Psycholinguistics"
  - id            : "2"
    institution   : "Centro de Investigaciones y Estudios Superiores en Antropología Social"
  - id            : "3"
    institution   : "University of Manitoba"

#author_note: |
#  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

abstract: |
  A hacer

keywords          : "Desarrollo de lenguaje, habla dirigida al niño, input lingüistico, Tseltal, Maya"
wordcount         : "XXXX (XXXX sin bibliografía)"

csl: apa-noissue.csl

bibliography      : ["Tseltal-CLE-full2015sample.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf #apa6_pdf or apa6_word
---

```{r load_packages, include=FALSE, echo=FALSE, warning=FALSE}
library(papaja)
library(ggplot2)
library(tidyverse)
library(viridis)
library(grid)
library(gridExtra)
library(lme4)
library(glmmTMB)
library(DHARMa)
library(bbmle)
library(broom.mixed)
source("../0-Helper.R")
```

```{r analysis_presets, include=FALSE}
options(scipen=999)
data.path <- "transcripts/anon/" # text files exported from ELAN
metadata.path <- "metadata/"
plot.path <- "plots/" # output plots
shiny.input.path <- "../shiny_input/Tseltal-CLE-full2015sample"
shiny.input.img.path <- "../www/Tseltal-CLE-full2015sample"
seg.index.file <- paste0(metadata.path, "Segment-order-inventory.csv")
ptcp.info.file <- paste0(metadata.path, "recording-info.csv")

convert_hhmmss_to_dt <- function(t) {
  dt <- lubridate::as_datetime(lubridate::hms(paste0(
    substr(t, 1, 2), ":", substr(t, 3, 4), ":", substr(t, 5, 6))))
  return(dt)
}

```

```{r prepare_data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Read in annotation files
files <- list.files(path = data.path,pattern="*.txt")
all.data <- data.frame()
for (i in 1:length(files)) {
#  print(files[i])
  newfile <- read_csv(paste0(data.path, files[i]),
                      col_types = cols(val = col_character()))
  newfile$child_id <- unlist(strsplit(files[i], '\\_'))[1]
  newfile$seg_start_tod <- convert_hhmmss_to_dt(
    unlist(strsplit(files[i], '\\_'))[2])
  newfile$seg_start_rec <- convert_hhmmss_to_dt(
    unlist(strsplit(files[i], '[\\_\\.]'))[3])
  all.data <- rbind(all.data, newfile)
}
all.data$row <- c(1:nrow(all.data))

# Read in supplementary data
ptcp.info <- read_csv(ptcp.info.file, col_types = cols()) %>%
  dplyr::select(c(aclew_id, child_level_id, sharing_environment,
                  lab_internal_subject_id, age_mo_round, child_sex,
                  mat_ed, fat_ed, std_length_of_recording, start_of_recording,
                  number_older_sibs, mother_age, father_age, household_size))

# Add mean and sd values for participant-level predictors to ptcp.info
ptcp.info <- ptcp.info %>%
  mutate(
    tchiyr.m = mean(age_mo_round),
    motyr.m = mean(mother_age),
    nsb.m = mean(number_older_sibs),
    hsz.m = mean(household_size),
    tchiyr.sd = sd(age_mo_round),
    motyr.sd = sd(mother_age),
    nsb.sd = sd(number_older_sibs),
    hsz.sd = sd(household_size)
    )

# Mini summary of annotated segments per rec
seg.info <- all.data %>%
  select(c(child_id, seg_start_tod)) %>%
  distinct() %>%
  group_by(child_id) %>%
  mutate(
    segment_num = row_number(),
    segment_dur_min = 5) %>%
  ungroup()

# Merge in participant and segment info to the main data table
all.data <- all.data %>%
  filter((tier == "CHI" | tier == "OTR") & !grepl("NO-HAY-PALABRAS", val)) %>%
  left_join(ptcp.info, by = c("child_id" = "lab_internal_subject_id")) %>%
  left_join(seg.info, by = c("child_id", "seg_start_tod"))

avg.utt.len.tseltal <- all.data %>%
  filter(tier == "OTR") %>%
  dplyr::select(dur) %>%
  summarise(mean.utt.len = mean(dur),
            median.utt.len = median(dur))
```

# Introducción

Alrededor del mundo, los niños aprenden su lengua materna a través de las interacciones verbales que observan y de las cuales en que participan, en el hogar y en la escuela. Estudios anteriores han establecido que el desarrollo del lenguaje sucede más temprano y se acelera más rapido si los cuidadores del niño hablan directa y frecuentemente con él, con un estilo apropriado para su nivel de sofisticación lingüístico y cognitivo [Habla Dirigida al Niño, HDN; REFS]. En particular, los niños que oyen más habla dirigida así a ellos desarrollan más rápidamente su conocimiento lexical; producen y compreden más palabras, y reconocen más rápidamente las palabras [REFS]. Sabemos también que el conocimiento lexical influye en la adquisición y uso del conocimiento sintáctico [REFS]. En resumidas palabras, el HDN es un mecanismo fundamental para aprender el lenguaje.

Sin embargo, este mecanismo no permite establecer la cantidad de HDN que es necesario para la adquisición del lenguaje. Estudios basados en interacciones cortas y modelos teóricos y computacionales, sugieren que la cantidad de evidencia lingüística requerida para el desarrollo normal del lenguaje sea inmenso. Pero evidencia sociolingüística y antropológica sugiere algo contrario, que (a) hay muchas maneras de acumular evidencia lingüística del ambiente familiar, que (b) hablar directamente a niños es muy común a través de las sociedades humánas, y que (c) mucha HDN es una invención moderna y occidental [REFS].

Para echar luz sobre la cantidad de evidencia lingüística requerida para el desarrollo del lenguaje, es necesario enfocar en los patrones de habla que los niños encuentran normalmente en sus hogares---patrones de habla cotidiana, y no solo HDN. El método ideal para estudiar patrones el la habla cotidiana alrededor del niño es usar grabaciones "daylong", en cual el bebé o niño lleve una camiseta o un chaleco con una grabadora adentro y sigue con un día en casa "normal", resultando en una grabación que, frecuentamente dura seis horas o más [REFS casillas cristia]. Con estas grabaciones, las cual son centrado en el perspectivo del niño, es posible documentar patrones en habla a través una una multiplicidad de actividades cotidianas y parejas (e.g., la madre, la tía, un niño vecino, etc.). La colección de grabaciones daylong es sencillo, y así es posible colectar, anotar, y analyzar grabaciones en una manera casi identical entre populaciones diversas.

Estimar la variación humana en ambientes lingúísticos de niños requiere que estudiamos las experiencias de niños criados en comunidades grandes y pequeñas, urbanas y rurales, modernas y tradicionales. En cambio, la mayoria de investigaciones cuantitativas de habla ambiental del niño viene de populaciones urbanas, occidentales, y de habla inglesa [REFS]. Por el contrario, estudios mostrando la diversidad de ambientes lingüísticos y de prácticas para la socializacíon de lengua han enfocado, en la mayor parte, en comunidades pequeñas y tradicionales, o en grupos subrepresentadas dentro de contextos urbanos o semi-urbanos mas grandes [REFS].

Investigaciones comparativas mas recientes sugieren que la cantidad de HDN en el ambiente de niños es muy poco, incluso contextos culturales en cual es típico hablar directamente a bebés sobre su foco de atención (en el estilo "child centric"; REFS). Antes del tres años, los niños oigan menos que cinco minutos de HDN de adultos durante un día normal a casa [REFS bunce]. Diferencias en ambiente lingüístico de niños emerge en *quien* habla al niño, antes bien la cantidad de HDN [REFS bunce]. Por ejemplo, Casillas et al., encontraron que la práctica de aloparenting entre familias en la Isla de Rossel (Papua Nueva Guinea) tiene un efecto en los patrones de habla oído por los niños: comparado con otras sociedades indígenas con estructuras asentamientos similares, y con populaciones urbanas y occidentales, niños jovenes en la Isla de Rossel oigan más habla de otro niños y de hombres [REFS casillas 2019 ur; bunce].

Una tema persistente en estes esudios de habla en el ambiente natural del niño es que colectar, transcribir, y anotar grabaciones muy naturales es muy caro y cuesta mucho tiempo; por eso hay una tendencia enfocar en muestras pequeñas (típicamente N = 20 y mas pequeño, a través de 3--5 años; REFS). En el caso de una comunidad subrepresentada, sea prematuro formar conclusiones fuertes en un basis de datos así pequeño; es facil imaginar que un analisis derivando de una muestra pequeña no representa suficientamente la variación normal en la comunidad y da una impresión inexacto de las tendencias típicas en el ambiente lingüístico de niños allá. 

En este estudio buscamos establecer la variación típica y tendencias in general del uso de HDN en una comunidad lingüística para que sólo una muestra pequeña de datos daylong ha estado analizado: el Tseltal de Tenejapa (Maya; Chiapas, Mexico). En esta comunidad, como en otras comunidades Mayas (e.g., Tsotil, Yukateko, K'iche', Mam), niños están socializados observar las interacciones alrededor de ellos (sin esperar a estar el foco de atención social) [REFS de leon, rogoff, pye, y shneidman]. Están llevados por la más parte del primo año de vida, primariamente por la madre; y mientras cuidadores respondan muy sensiblemente cuando el bebé quiere amamantar, dormir, sentarse, o tener un cambio de pañal/pantalon, no usan HDN frecuentamente [REFS]. Este estilo de interaccion con niños "non-child-centric" se encuentra en muchas comunidades alrededor del mundo [REFS]. También es común que un bebé o niño joven está cuidado por un hermano mayor o otros miembros de la familia, especialmente después de que empiezan comer comida solida; Brown estima que, después de tres años, la mayor parte del HDN viene de otros niños (HDN-N), y no de adultos. En unas comunidades Yukatekas, Shneidman también encontró que la cantidad de HDN-N aumentó mucho (300%) entre uno y tres años, y formó la mayoría del HDN de niños 2 años y más.

Un estudio anterior ha usado grabaciones daylong con niños tseltales para estimar la cantidad de HDN y otra habla oíble [REFS], confirmando que niños sur la edad de tres años les están directamente hablado infrecuentamente---3.6 minutos por hora---sin evidencia de demora en su desarrollo lingüístico. El HDN en el ambiente vino, por la mayor parte (~80%) de mujeres, con un pequeño y non-significo aumentación de HDN-N asociado con edad del niño mas alta. Sin embargo, estos resultados están basados en las grabaciónes de sólo 10 niños, y sólo con niños menor que tres años; tan joven para observar el inicio de HDN-N frecuente [REFS]. La muestra pequeña puede también explicar, en parte, la discrepancia en la prevalencia de HDN-N entre eso estudio y lo de Shneidman en Goldin-Meadow (2012), en cual HDN-N fue muy frecuente después de 2 años. Sin una muestra mas integral, es dificil saber si la diferencia deriva de prácticas diferentes entre comunidades Tseltales y Yukatecos, de métodos de grabación, o algo diferente.

Presentamos aquí una replicación y extensión considerable del estudio de Casillas et al. (2019): investigamos la velocidad de HDN usado por cuidadores adultos y jovenes con 56 niños tseltales entre 2 y 52 meses de edad, incluyendo los 10 niños destacados en el estudio anterior. Usando lo mismo técnico---anotar y transcribir segmentos cortos aleatoriamente del día de grabar---esperábamos que (a) in general, la velocidad de HDN no cambia significamente con la edad del niño, (b) HDN de otros niños aumenta significamente con la edad del niño y, como antes, (c) niños encuentran HDN más frecuentamente en la mañana, con niños más grande oyendo mas HDN cercal del mediodía.<!-- Especulamos también que niños que oigaron más HDN tendrían vocabularios productivos y receptivos más grandes. Testamos esta predicción indirectamente por relacionar la velocidad de HDN de niños individuales con la diversidad de vocbaulario en su habla spontanea de los segmentos transcribados.-->

# Metodología

Los niños enfocados aquí vienen de una comunidad tradicional con una agricultura de subsistencia situada en los altos de Chiapas (en el sur de México). Antes de que entran en la escuela, el desarrollo lingüístico de niños en esta comunidad es, típicamente, monolingual en el Tseltal, una idioma Maya [REFS]. Hogares son organizados en grupos patrilocales, en cuales viven miembros de la familia de varias generaciones. Durante las horas despiertas del día, infantes están llevados por un rebozo en la espalda de sus madres, mientras ella sigue con sus actividades diarias. Si la madre va a trabajar en el campo, a veces trae el bebé, y a veces deja el bebé con un otro miembro de la familia en casa (e.g., una tía o hermano mayor del niño). Todos los miembros de la familia (~4 años y más) contribuyen al cuidado de niños [REFS].

Décadas de investigación antropológica y lingüística ha establecido que el entorno lingüístico de niños Mayas no está centrado en el interes del niño o en los nombres de objetos; por el contrario, niños están socializados pagar atención a la interacción social entre otros, tomando parte en la interacción como participante lateral [REFS @brown1998conversational; @brown2011cultural; @brown2014interactional]. Durante la infancia, bebés reciben respuestas rápidas y efectivas cuando indican que tienen hambre, quieren dormir, y otros asuntos corporeales. Más tarde, cuando empiezan a comunicar con gestos y palabras reconocibles, provocan respuestas verbales mas frecuentamente de sus cuidadores [REFS].

<!--
Typically, TCDS is limited until children themselves begin to initiate interactions, usually around age 1;0. Interactional exchanges, when they do occur, are often brief or non-verbal (e.g., object exchange routines) and take place within a multi-participant context [@brown2014interactional]. Interactions tend to focus on appropriate actions and responses (not on words and their meanings), and young children are socialized to attend to the activities taking place around them [see also @deleon2011language; @rogoff2003firsthand]. By age five, most children are competent speakers who engage in daily chores and the caregiving of their younger siblings. The Tseltal approach to caregiving is similar to that described for other Mayan communities [e.g., @deleon2011language; @gaskins2000childrens; @pye1986quiche; @rogoff2003firsthand; @shneidman2012language].

NOT USED: That said, other properties of Tseltal CDS may facilitate word and language learning, including conversational repetition and semantically specific verbs [@brown2011cultural]. Infants are rarely put on the ground. Therefore, children can't usually pick up the objects around them until they are old enough to walk. Toys are scarce and books are vanishingly rare, so the objects children do get their hands on tend to be natural or household objects (e.g., rocks, sticks, spoons, baskets, etc.).

The current data come from the Casillas HomeBank Corpus [@Casillas-HB], which includes raw daylong recordings and other developmental language data from more than 100 children under 4;0 across two small-scale, traditional indigenous communities: the Tseltal Mayan community described here and a Papua New Guinean community described elsewhere [@brown2011cultural; @brown2014interactional]. This Tseltal corpus, primarily collected in 2015, includes raw recordings from 55 children born to 43 mothers. The participating families typically only had 2 to 3 children (median = 2; range = 1--9), due to the fact that they come from a young subsample of the community (mothers: mean = 26.3 years; median = 25; range = 16--43 and fathers: mean = 30; median = 27; range = 17---52). Based on the ages of living children, we estimate that, on average, mothers were 20 years old when they had their first child (median = 19; range = 12--27), with a following average inter-child interval of 3 years (median = 2.8; range = 1--8.5). Twenty-eight percent of the participating families had two children under 4;0. Household size, defined in our dataset as the number of people sharing a kitchen or other primary living space, ranged between 3 and 15 people (mean = 7.2; median = 7). Although 32.7% of the target children are first-born, they were rarely the only child in their household. Most mothers had finished primary school (37%; 6 years of education) or secondary school (30%; 9 years of education), with a few more having completed preparatory school (12%; 12 years of education) or some university-level training (2% (one mother); 16 years of education); the remainder (23%) had no schooling or did not complete primary school. All fathers had finished primary school, with most completing secondary school (44%) or preparatory school (21%), and two completing some university-level training (5%). To our knowledge at the time of recording, all children were typically developing.

NOT USED: While 93% of the fathers grew up in the village where the recordings took place, only 53% of the mothers did because of the way clan membership influences marriage and land inheritance.

When possible, we collected dates of birth for children using a medical record card typically provided by the local health clinic within two weeks of birth. However, some children do not have this card. Cards are also sometimes created long after a child’s birth. We asked all parents to also tell us the approximate date of birth of the child, the child's age, and an estimate of the time between the child's birth and creation of the medical record card. We used these multiple sources of information to triangulate the child's most likely date of birth if the medical record card appeared to be unreliable, following up for more details from the families if necessary.

We used a novel combination of a lightweight stereo audio recorder (Olympus WS-832) and wearable photo camera (Narrative Clip 1) fitted with a fish-eye lens to track children's interactions over the course of a 9--11-hour period at home in which the experimenter was not present. Ambulatory children wore both devices at once (as shown in [Figure 1](#fig1)) while other children wore the recorder in a onesie while their primary caregiver wore the camera on an elastic vest. The camera was set to take photos at 30-second intervals and was synchronized to the audio in post-processing to generate snapshot-linked audio (media post-processing scripts at: https://github.com/marisacasillas/Weave). We used these recordings to capture a wide range of the linguistic patterns children encounter as they participate in different activities over the course of their day [@bergelson2018day; @greenwood2011assessing; @tamislemonda2018routine]. Participant consent processes and data collection were conducted in accordance with ethical guidelines approved by the Radboud University Social Sciences Ethics Committee.

## Data selection and annotation {#methods-samples}
Although the Tseltal corpus contains more than 500 hours of raw photo-linked audio, very little of it is useful without adding manual annotation. We estimated that we could fully transcribe approximately 10 hours of the corpus over the course of three 6-week field stays in the village between 2015 and 2018, given full-time help from a native member of the community on each trip. This estimate was approximately correct: average exhaustive transcription time for one minute of audio was around 50 minutes, given that many clips featured overlapping multi-speaker talk and/or significant background noise. Given the resource-intensive nature of annotation, we strategically sampled clips in a way that would let us ask about age-related changes in children's language experience, but with enough data per child to generate accurate estimates of their individual speech environments. Our solution was as follows:

We chose 10 children's recordings based on maximal spread in child age (0;0--3;0), child sex, and maternal education ([Table 1](#tab1); all had native Tseltal-speaking parents). We selected one hour's worth of non-overlapping clips for transcription from each recording in the following order: nine randomly selected 5-minute clips, five manually selected 1-minute top 'turn-taking' clips, five manually selected 1-minute top 'vocal activity' clips, and one manually selected 5-minute extension of the ‘best’ 1-minute clip (i.e., the clip with the most variable, most voluble interactive language use for that recording see Figure 2 for the clip distribution within recordings). The idea in creating these different subsamples was to measure properties of (a) children's _average_ language environments, (b) children's most _interactive-input-dense_ language environments, and (c) children's most _mature vocal behavior_, with these three sub-samples known as the "random", "turn-taking", and "vocal activity" samples, respectively. All the samples were taken between the moment the experimenter departed and the moment she returned.

The turn-taking and high-activity clips were chosen by two trained annotators (the first author and a student assistant) who listened to each raw recording in its entirety at 1--2x speed while actively taking notes about potentially useful clips. The first author then reviewed the list of candidate clips and chose the best five 1-minute samples for each of the two activity types. Note that, because the manually selected clips did not overlap with the initial "random" clip selection, the "true" peak turn-taking and vocal-activity clips for the day could have possibly occurred during the random clips. High-quality turn-taking activity was defined as closely timed sequences of contingent vocalization between the target child and at least one other person (i.e., frequent vocalization exchanges). High-quality vocal activity clips were defined as periods in which the target child produced the most and most diverse spontaneous (i.e., not imitative) vocalizations (full instructions at https://git.io/fhdUm).

The 10 hours of clips were then jointly transcribed and annotated by the first author and a native speaker of Tseltal who personally knows all the recorded families. Transcription was done in ELAN [@ELAN] using the ACLEW Annotation Scheme [full documentation at https://osf.io/b2jep/wiki/home/, @casillas2017ACLEWDAS]. Utterance-level annotations included: an orthographic transcription (Tseltal), a loose translation (Spanish), a vocal maturity rating for each target child utterance (non-linguistic/non-canonical babbling/canonical babbling/single words/multiple words), and the intended addressee type for all non-target-child utterances (target-child/other-child/adult/adult-and-child/animal/other-speaker-type). Intended addressee was determined using contextual and interactional information from the photos, audio, and preceding and following footage; utterances with no clear intended addressee were marked as 'unsure'. We annotated lexical utterances as single- or multi-word based on the word boundaries provided by the single native speaker who reviewed all transcriptions. Note that Tseltal is a mildly polysynthetic language, so words typically contain multiple morphemes. We did not annotate individual activity types in the clips; we instead use time of day as a proxy for the activities and daily routines associated with subsistence farming and family life in this community (see above).

## Data analysis {#methods-analysisinfo}
In what follows we first describe Tseltal children's speech environments based on the nine randomly selected 5-minute clips from each child. We investigate the effects of child age, time of day, household size, and number of speakers on both TCDS min/hr and ODS min/hr. We then repeat these analyses, only now looking at the high "turn-taking" clips. Finally, we wrap up by outlining a coarse trajectory of Tseltal children's early vocal development.

## Statistical models
All analyses were conducted in R with generalized linear mixed-effects regressions using the glmmTMB package, and all plots were generated with ggplot2 [@brooks2017modeling; @R-ggplot2; @R-base]. All data and analysis code can be found at https://github.com/marisacasillas/Tseltal-CLE Notably, both speech environment measures are naturally restricted to non-negative (0--infinity) values. This implicit boundary restriction at zero causes the distributional variance of the measures to become non-gaussian (i.e., with a long right tail). We handle this issue by using a negative binomial linking function in the regression, which estimates a dispersion parameter (in addition to the mean and variance) that allows the model to more closely fit our non-negative, overdispersed data [@brooks2017modeling; @smithson2013generalized]. When, in addition to this, extra cases of zero were evident in the distribution (e.g., TCDS min/hr was zero because the child was alone), we also added a zero-inflation model to the regression. A zero-inflation negative binomial regression creates two models: (a) a binary model to evaluate the likelihood of none vs. some presence of the variable (e.g., no vs. some TCDS) and (b) a count model of the variable (e.g., '3' vs. '5' TCDS min/hr), using the negative binomial distribution as the linking function. Alternative, gaussian linear mixed-effects regressions with logged dependent variables are available in the Supplementary Materials, but the results are broadly similar to what we report here.
-->


## Participantes

## Recolección de datos

## Anotación de datos

# Resultados

# Discusión

<!--
Census notes
de: http://webcache.googleusercontent.com/search?q=cache:BHXsAGj22NgJ:www.microrregiones.gob.mx/catloc/contenido.aspx?refnac%3D070930014&hl=en&gl=nl&strip=1&vwsrc=0

Año	2005	2010
Datos demográficos	Hombres	Mujeres	Total	Hombres	Mujeres	Total
Total de población en la localidad	557	542	1,099	560	556	1,116
Viviendas particulares habitadas	182	217
Grado de marginación de la localidad (Ver indicadores)	Alto	Alto
Grado de rezago social localidad (Ver indicadores)	3 medio	Medio
Indicadores de carencia en vivienda (Ver indicadores)	
-->

# Agradecimientos {#acknowledgements}
Agredecemos y reconocemos Rebeca Guzmán López, Humbertina Gómez Pérez, e Antun Gusman Osil, los quienes hicieron posible la colección, anotación, y transcripción de estes datos. Acknowledgements también las familias participantes y la comunidad tseltal para su apoyo. Esta investigación fue financiado por una beca NWO Veni (275-89-033) de MC, una beca XXX de MS, fundos para trabajo de campo del Max Planck Institute for Psycholinguistics, y con el apoyo del Centro de Investigaciones y Estudios Superiores en Antropología Social (CIESAS) Sureste. Este manuscrito fue escrito con el library papaja en RStudio [@R-papaja].

\newpage

# Bibliografía {#refs}

```{r create_r-references}
r_refs(file = "Tseltal-CLE-full2015sample.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
