---
title             : "Título"
shorttitle        : "Título corto"

author: 
  - name          : "Marisa Casillas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "P.O. Box 310, 6500 AH Nijmegen, The Netherlands"
    email         : "Marisa.Casillas@mpi.nl"
  - name          : "Juan Méndez Girón"
    affiliation   : "2"
  - name          : "Penelope Brown"
    affiliation   : "1"
  - name          : "Gilles Polian"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Max Planck Institute for Psycholinguistics"
  - id            : "2"
    institution   : "Centro de Investigaciones y Estudios Superiores en Antropología Social"

#author_note: |
#  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

abstract: |
  A hacer

keywords          : "Desarrollo de lenguaje, habla dirigida al niño, input lingüistico, Tseltal, Maya"
wordcount         : "XXXX (XXXX sin bibliografía)"

csl: apa-noissue.csl

bibliography      : ["Tseltal-CLE-full2015sample.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf #apa6_pdf or apa6_word
---

```{r load_packages, include=FALSE, echo=FALSE, warning=FALSE}
library(papaja)
library(ggplot2)
library(tidyverse)
library(viridis)
library(grid)
library(gridExtra)
library(lme4)
library(glmmTMB)
library(DHARMa)
library(bbmle)
library(broom.mixed)
source("../0-Helper.R")
```

```{r analysis_presets, include=FALSE}
options(scipen=999)
data.path <- "transcripts/anon/" # text files exported from ELAN
metadata.path <- "metadata/"
plot.path <- "plots/" # output plots
shiny.input.path <- "../shiny_input/Tseltal-CLE-full2015sample"
shiny.input.img.path <- "../www/Tseltal-CLE-full2015sample"
seg.index.file <- paste0(metadata.path, "Segment-order-inventory.csv")
ptcp.info.file <- paste0(metadata.path, "recording-info.csv")

convert_hhmmss_to_dt <- function(t) {
  dt <- lubridate::as_datetime(lubridate::hms(paste0(
    substr(t, 1, 2), ":", substr(t, 3, 4), ":", substr(t, 5, 6))))
  return(dt)
}

```

```{r prepare_data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Read in annotation files
files <- list.files(path = data.path,pattern="*.txt")
all.data <- data.frame()
for (i in 1:length(files)) {
#  print(files[i])
  newfile <- read_csv(paste0(data.path, files[i]),
                      col_types = cols(val = col_character()))
  newfile$child_id <- unlist(strsplit(files[i], '\\_'))[1]
  newfile$seg_start_tod <- convert_hhmmss_to_dt(
    unlist(strsplit(files[i], '\\_'))[2])
  newfile$seg_start_rec <- convert_hhmmss_to_dt(
    unlist(strsplit(files[i], '[\\_\\.]'))[3])
  all.data <- rbind(all.data, newfile)
}
all.data$row <- c(1:nrow(all.data))

# Read in supplementary data
ptcp.info <- read_csv(ptcp.info.file, col_types = cols()) %>%
  dplyr::select(c(aclew_id, child_level_id, sharing_environment,
                  lab_internal_subject_id, age_mo_round, child_sex,
                  mat_ed, fat_ed, std_length_of_recording, start_of_recording,
                  number_older_sibs, mother_age, father_age, household_size))

# Add mean and sd values for participant-level predictors to ptcp.info
ptcp.info <- ptcp.info %>%
  mutate(
    tchiyr.m = mean(age_mo_round),
    motyr.m = mean(mother_age),
    nsb.m = mean(number_older_sibs),
    hsz.m = mean(household_size),
    tchiyr.sd = sd(age_mo_round),
    motyr.sd = sd(mother_age),
    nsb.sd = sd(number_older_sibs),
    hsz.sd = sd(household_size)
    )

# Mini summary of annotated segments per rec
seg.info <- all.data %>%
  select(c(child_id, seg_start_tod)) %>%
  distinct() %>%
  group_by(child_id) %>%
  mutate(
    segment_num = row_number(),
    segment_dur_min = 5) %>%
  ungroup()

# Merge in participant and segment info to the main data table
all.data <- all.data %>%
  filter((tier == "CHI" | tier == "OTR") & !grepl("NO-HAY-PALABRAS", val)) %>%
  left_join(ptcp.info, by = c("child_id" = "lab_internal_subject_id")) %>%
  left_join(seg.info, by = c("child_id", "seg_start_tod"))

avg.utt.len.tseltal <- all.data %>%
  filter(tier == "OTR") %>%
  dplyr::select(dur) %>%
  summarise(mean.utt.len = mean(dur),
            median.utt.len = median(dur))
```

# Introducción

Alrededor del mundo, los niños aprenden su lengua materna a través de las interacciones verbales que observan y de las cuales en que participan, en el hogar y en la escuela. Estudios anteriores han establecido que el desarrollo del lenguaje sucede más temprano y se acelera más rapido si **los padres** del niño hablan directa y frequentemente con él, con un estilo apropriado para su nivel de sofisticación lingüístico y cognitivo [Habla Dirigida al Niño, HDN; REFS]. En particular, los niños que oyen más habla dirigida así a ellos desarrollan más rápidamente su conocimiento lexical; producen y compreden más palabras, y reconocen más rápidamente las palabras [REFS]. Sabemos también que el conocimiento lexical influye en la adquisición y uso del conocimiento sintáctico [REFS]. En resumidas palabras, el HDN es un mecanismo fundamental para aprender el lenguaje.

Sin embargo, este mecanismo no permite establecer la cantidad de HDN que es necesario para la adquisición del lenguaje. Estudios basados en interacciones cortas y modelos teóricos y computacionales, sugieren que la cantidad de evidencia lingüística requerida para el desarrollo normal del lenguaje sea inmenso. Pero evidencia sociolingüística y antropológica sugiere algo contrario, que (a) hay muchas maneras de acumular evidencia lingüística del ambiente familiar, que (b) hablar directamente a niños es muy común a través de las sociedades humánas, y que (c) mucha HDN es una invención moderna y occidental [REFS].


* To better understand how much linguistic evidence is needed to support child language development, we need to estimate how much speech children hear in their everyday lives. Further, we need to make these estimates across diverse language communities around the world, in order to unveil the range of normal variation for human language development. Most work using quantitative methods to estimate input have come from urban, Western communities. And studies demonstrating diversity in child language environments and approaches to child language socialization have come more often from small scale, traditional communities or ethnic sub-communities within larger-scale urban and semi-urban contexts [REFS].

* Recent comparative work suggests that the quantity of HDN that children encounter in their everyday life at home is much lower than previously thought. Even in urban and non-urban communities documented to have a very child-centric style of early interaction, children before age three tend to hear fewer than 5 minutes of directed talk from adults during their waking hours at home [REFS bunce].

* Cross-culturally, differences in linguistic input appear more apparent in *who* talks to the child, rather than how much input the child hears (John study). For example, Casillas and colleagues found that the alloparenting practices documented in prior ethnographic work on Rossel Island, Papua New Guinea were evident in patterns of talk to children: compared to both other, unrelated indigenous societies with patrilocal settlement structures (REFS) and to modern urban Western populations (REFS), young children and infants on Rossel Island heard proportionally more speech from other children and from adult men.

* A persistent issue, however, is that collecting, transcribing, and annotating highly naturalistic data for analysis is expensive and time consuming, and therefore the samples tend to be small, i.e., N = 20 and smaller, typically cross-sectionally sampled over a multi-year age range (Shneidman is an exception). For underrepresented communities in particular, drawing strong conclusions from such limited samples is not warranted; it is easy to imagine that the initial analysis underrepresents typical variation in the community and gives an inaccurate impression of the overall tendencies in the community.

* In the present study we seek to better establish typical variation and overall tendencies of HDN usage in one language community for which only a small sample of data was previously availabe: Tenejapan Tseltal. Work from linguistic anthropologist Brown has reported that, similar to several other Mayan communities, Tseltal caregivers raise their children to become keen observers of the interactions going on around them (i.e., non-child-centric). ... add in more here, also from de leon, rogoff, pye, and shneidman ... More recently Casillas and colleagues used daylong recordings to follow up on these ethographic findings, showing that indeed children under three were only spoken to infrequently, at a rate of 3.6 minutes per hour, yet showed no evidence of developmental language delay. Further, they found no evidence for frequent input from other children; 80% of HDN came from women, with a small but non-significant increasing proportion from other children. However, their results were based on recordings from 10 children, and only on children up until age 3;0, an age range too young to observe frequent HDN from other children (REFS Brown). The limited sample size and age range may also help explain some of the unexpected discrepancies between the findings for Tseltal (Casillas) and Yukateko (Shneidman), which otherwise could derive from a combination of differences in researcher recording method and caregiver interactional practices.

* We replicate and expand Casillas et al.'s study by investigating the rate of HDN among XX Tseltal children between ages XX and XX, including the 10 from the original study. Using the same technique of randomly sampling audio clips from a whole waking day at home, we expected to find that (a) the overall rate of HDN does not change significantly with age, (b) HDN from other children increases significantly with age, and, as before (c) most HDN is encountered in the morning, with older children more often hearing HDN midday. We also speculated that children who hear more HDN have larger productive and receptive vocabularies. We indirectly test this prediction by relating individual children's HDN rate to the diversity of vocabulary in their spontaneous speech during the sampled clips.

# Acknowledgements {#acknowledgements}
<!--We thank and acknowledge Rebeca Guzmán López, Humbertina Gómez Pérez, and Antun Gusman Osil, who helped make the collection and annotation of these recordings possible. We are also enormously grateful to the participating families and to the community at large for their support. This work is supported by a NWO Veni Innovational Scheme grant (275-89-033) to MC, by XXX Melanie grant, and by fieldwork and transcription funding from the Max Planck Institute for Psycholinguistics. This paper was written using the papaja library in RStudio [@R-papaja].-->

\newpage

# References {#refs}

```{r create_r-references}
r_refs(file = "Tseltal-CLE-full2015sample.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
