---
title             : "Child language experience in a Tseltal Mayan village"
shorttitle        : "Child language experience in a Tseltal Mayan village"

author: 
  - name          : "Marisa Casillas"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "P.O. Box 310, 6500 AH Nijmegen, The Netherlands"
    email         : "Marisa.Casillas@mpi.nl"
  - name          : "Penelope Brown"
    affiliation   : "1"
  - name          : "Stephen C. Levinson"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Max Planck Institute for Psycholinguistics"
#  - id            : "2"
#    institution   : "Cambridge University"

#author_note: |
#  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "Child-directed speech, Linguistic input, Non-WEIRD, Vocal maturity, Turn taking"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include=FALSE, echo=FALSE, warning=FALSE}
library(papaja)
library(ggplot2)
library(tidyverse)
library(viridis)
library(grid)
library(gridExtra)
library(ggpirate)
source("0-Helper.R")
```

```{r analysis_presets, include=FALSE}
data.path <- "transcripts/anon/" # text files exported from ELAN
plot.path <- "plots/" # output plots
seg.index.file <- "Segment-order-inventory.csv"
ptcp.info.file <- "recording-info.csv"
samplelabels <- c("High activity  ", "Random  ")
col.sample.bu <- list(
  scale_fill_manual(labels=samplelabels, values=viridis(2)),
  scale_color_manual(labels=samplelabels, values=viridis(2)))
col.sample.bu3 <- list(
  scale_fill_manual(labels=samplelabels, values=viridis(3)),
  scale_color_manual(labels=samplelabels, values=viridis(3)))
allowed.overlap <- 1000 #ms
allowed.gap <- 2000 #ms
sem <- function (x) {
    sd(x) / sqrt(length(x))
}
```

# Introduction {#intro}
A great deal of work in developmental language science revolves around one central question: What linguistic evidence (i.e., what types and how much) is needed to support first language acquisition? In pursuing this topic, many researchers have fixed their sights on child-directed speech (CDS), showing that it is linguistically distinctive (REFS)**[TASK 00: Add missing references]**, interactionally rich (REFS), preferred by infants (REFS), and---perhaps most importantly---facilitates word learning (REFS). One might then conclude that CDS is an essential component for acquiring a first language. Yet ethnographic reports from a number of traditional, non-Western communities suggest that children easily acquire their community's language(s) with little or no CDS (REFS). If so, CDS may not be essential for learning language; just useful for facilitating certain aspects of language development. In this paper we investigate the language environment and early development of 10 Tseltal Mayan children growing up in a community that reportedly uses very little CDS with infants and young children (REFS Brown).

## Child-directed speech  {#intro-cds}
The amount of CDS children hear influences their language development, particularly their vocabulary (REFS). For example, **[TASK 01: Add examples of input-vocab link]**. CDS has also been linked to young children's speed of lexical retrieval (REFS Weisleder; LuCiD) and syntactic development (REFS Huttenlocher). **[TASK 02: Read Huttenlocher and add details here]**. The conclusion drawn from much of this work is that CDS is an ideal register for learning words---especially concrete nouns and verbs---because it is tailored to maximize a child's moment-to-moment interest and understanding (REFS).  Indeed, even outside of first-person interaction, infants and young children prefer listening to CDS over adult-directed speech (REFS ManyBabies, etc.), suggesting that CDS is useful in catching, maintaining, and focusing children's attention. There are, however, a few significant caveats to the body of work relating CDS quantity to language development.

First, while there is overwhelming evidence linking CDS quantity to vocabulary size, links to grammatical development are more scant (REFS: Huttenlocher; Frank et al.). Children must master the systemic underpinnings of their language(s), e.g., the phonology, morphology, and syntax. While the advantage of CDS for referential word learning is clear, it is less obvious how CDS facilitates syntactic learning. **[TASK 03: Add argument from Yurovsky paper + refrences therein]** On the other hand, there is a wealth of evidence that both children and adults' syntactic knowledge is highly lexically specified (REFS), and that, crosslinguistically, children's vocabulary size is one of the most robust predictors of their early syntactic development (REFS). In short, what is good for the lexicon may also be good for syntax. For now, however, the link between CDS and other aspects of grammatical development still needs to be more thoroughly tested.

Second, **[TASK 04: Add paragraph on burstiness]**

Third, prior work has typically focused on Western (primarily North American) populations, limiting our ability to generalize these effects to children acquiring language worldwide (REFS: WEIRD; Lieven, 1994). While we do gain valuable insight by looking at _within-population_ variation (e.g., REFS), we can more effectively find places where our assumptions break down by studying _new_ populations. Linguistic anthropologists working in non-Western communities have long reported that caregiver interaction styles vary immensely from place to place, with some caregivers using little or no CDS to young children (REFS Gaskins, 2006). Children in these communities reportedly acquire language with 'typical'-looking benchmarks. For example, they start pointing (REFS Liszkowski) and talking (REFS Rogoff et al., 2003?; Brown??) around the same time we would expect for Western middle-class infants. These findings have had little impact on mainstream theories of word learning and language acquisition, partly due to a lack of directly comparable measures (Brown, 2014). If, however, these children indeed acquire language without delay despite little or no CDS, we must reconsider what kind of linguistic evidence is necessary for children to learn language.

<!--**[TASK 05: Check out previous ethnographic work]** Possibly relevant: Schieffelin, 1990; Ochs, 1988; Demuth, 1992(?); Takada, 2005; Goody, 1982; Schieffelin & Ochs, 1986; Pye, 1986; Gaskins, 2006; Brown & Casillas, under review).--> <!--Pye 1986. Quiché mayan speech to children. Journal of Child Language, 13(1), 85-100-->

## Language development in non-WEIRD communities {#intro-nonweird}
To our knowledge, only a handful of researchers have used methods from developmental psycholinguistics to describe the language environments and linguistic development of children growing up in traditional, non-Western communities. We focus here on _quantitative_ language development measures because the key claims about CDS and linguistic development are themselves quantitative in nature. We briefly highlight two recent efforts along these lines, but see Cristia et al. (2017) for a recent review.

Scaff, Cristia, and colleagues (REFS 2017; in preparation) have used a number of methods to estimate how much speech children hear in a Tsimane forager-horticulturalist population in the Bolivian lowlands. Their daylong recordings show that Tsimane children between 0;6 and 6;0 hear ~5 minutes of CDS per hour, with no increase for older children (but see Cristia et al., 2017). For comparison, children from North American homes between ages 0;3 and 3;0 are estimated to hear ~11 minutes of CDS per hour in daylong recordings (REFS: Bergelson, Casillas, et al., see also REFS the newer Tamis-LeMonda paper; maybe give estimates w/ age ranges for each??). In addition to CDS, Tsimane children also hear ~10 minutes of other-directed speech per hour (e.g., talk between adults)---more than the ~7 minutes of adult-directed speech per hour North American children are estimated to hear (REFS Bergelson, Casillas, et al.). This difference may be attributable to the fact that the Tsimane live in extended family clusters of 3--4 households, and so speakers are typically in close proximity to 5--8 other people (REFS Cristia et al., 2017).

Laura Shneidman and colleagues (REFS; 2010; 2012) analyzed speech from 1-hour at-home video recordings of children between ages 1;0 and 3;0 in two communities: Yucatec Mayan (Southern Mexico) and North American (in a major US city). Their analyses yielded four main findings: compared to the American children, (a) the Yucatec children heard many fewer utterances per hour, (b) a much smaller proportion of the utterances they heard were _child-directed_, (c) the proportion of utterances that were child-directed increased dramatically with age, matching U.S. children's by 3;0 months, and (d) most of the added CDS came from other children (e.g., older siblings and cousins). They also demonstrated that the lexical diversity of the CDS they hear at 24 months---particularly from adult speakers---predicted children's vocabulary knowledge at 35 months.

These groundbreaking studies establish a number of important findings: First, children in each of these communities appear able to acquire their languages with relatively little CDS. Second, CDS may become more frequent as children get older, though this may be largely due to speech from other children. Finally, despite these differences, CDS from adults may still be the most robust predictor of vocabulary growth.

## The current study {#intro-currentstudy}
We examine the early language experience of 10 Tseltal Mayan children under age 3;0. Prior ethnographic work suggests that Tseltal caregivers do not frequently speak directly to their children until the children themselves begin speaking (REFS: Brown??). Nonetheless, Tseltal children develop language with no apparent delays. Tseltal Mayan language and culture has much in common with the Yucatec Mayan communities Shneidman has worked with (REFS: 2010 + add other stuff that's not nec lg), which allows us to compare differences in child language environments between the two sites more directly than before.\footnote{For a review of comparative work in developmental linguistic anthropology, particularly on Mayan cultures, see Pye (2017).) We provide more details on this community and dataset in the [Methods section](#methods).

Similar to previous work by Shneidman, Scaff, Cristia, and colleages, we estimated how much speech children overheard, how much was directed to them, and how those quantities changed with age. To this foundation we added new sampling techniques for investigating variability in children's speech environments within daylong recordings. We also analyzed children's early vocal productions, examining both the overall developmental trajectory of their vocal maturity and how their vocalizations are influenced by CDS.

Based on prior work, we predicted that Tseltal Mayan children hear little CDS, that the amount of CDS they hear increases with age, that most CDS comes from other children, and that, despite this, Tseltal Mayan children would hit early speech production benchmarks on par with Western children. We additionally predicted that children's language environments would be bursty---that brief, high-intensity interactions would be sparsely distributed throughout the day, accounting for the majority of children's daily CDS---and that children's responsiveness and vocal maturity would be maximized during these moments of high-intensity interaction.

# Methods {#methods}
## Community {#methods-community}
The children in our dataset (REFS: Casillas HomeBank) come from a small-scale, subsistence farming community in the highlands of Chiapas in Southern Mexico. The vast majority of children grow up speaking Tseltal monolingually at home. Primary school is conducted in Tseltal, but secondary and further education is primarily conducted in Spanish. Nuclear families are often large (5+ children) and live in patrilineal clusters. Nearly all families grow staple crops such as corn and beans, but also bananas, chilies, squash, coffee, and more. <!--Families also cultivate and collect a range of other local plants, raise poultry for eggs and meat and, very occasionally, raise other animals (e.g., bulls) for slaughter. Additional produce, meat, and processed foods are available for purchase at small local shops and from vendors driving through town.--> Household and farming work is divided among men, women, and older children. Women do much of the daily cleaning and food preparation, but also frequently work in the garden, haul water and firewood, and do other physical labor. A few community members---both men and women---earn incomes as teachers and shopkeepers but are still expected to regularly contribute to their family's household work.

More than forty years of ethnographic work by the second author has told us that Tseltal children's language environments are non-child-centered and non-object-centered (REFS). During their waking hours, Tseltal infants are typically tied to their mother's back while she goes about her work for the day. Infants receive very little direct speech until they themselves begin to initiate interactions, usually as they approach their first birthdays. Even then, interactional exchanges are often brief or non-verbal (e.g., object exchange routines) and take place within a multi-participant context (Brown 2011; 2014). Rarely is attention given to words and their meanings, even when objects are central to the activity. Instead, interactions tend to focus on appropriate actions and responses, and young children are socialized to attend to the interactions taking place around them (REFS see also Rogoff and de Leon).

Young children are often cared for by other family members, especially older siblings. Even when not on their mother's back, infants are rarely put on the ground, so they can't usually pick up the objects around them until they are old enough to walk. Toys are scarce and books are vanishingly rare, so the objects children do get their hands on tend to be natural or household objects (e.g., rocks, sticks, spoons, baskets, etc.). By age five, most children are competent speakers who daily engage in chores and caregiving of their younger siblings. The Tseltal approach to caregiving is similar to that described for other Mayan communities (e.g., REFS Rogoff, Gaskins, de Leon, Shneidman).

## Corpus and data selection {#methods-corpus}
The current data come from the Casillas HomeBank Corpus (REFS HomeBank), which includes daylong recordings and other developmental language data from 55+ children under 4;0 in two indigenous, non-WEIRD communities: the Tseltal Mayan community described here and a Papua New Guinean community described elsewhere (REFS). The Tseltal data include recordings from 55 children born to 43 mothers. Our dataset, initiated in 2015, included  2.86 children per mother; median = 2; range = 1==9). 



55 children 48 mo and younger from 43 mothers
Average number of children per mother: 2.86 (range=1–9; median=2)
26% of families with two children under 48 months
Average age of 20.1 at first birth (range=12–27; median=19)
Average time between births: 3.04 years (range=1–8.5; median=2.8)

26.9 
range=16.6–43.8
median=25.9
Primary school
range=None–University
53%

30.5
range=17.7–52.9
median=27.6
Secondary school
range=Primary–University
93%

Extended households in our dataset (defined as those who share a kitchen or other primary living space) ranged between between 3 and 15 people *[TASK 06: Check this range]*. 
<!--Methods for estimating the quantity of speech that children hear have advanced significantly in the past two decades, with long-format (4+ hour) at-home audio recordings quickly becoming the new standard (e.g., with the LENA^®^ system; REFS). These recordings capture the range of linguistic patterns children hear as they participate in different activities with different speakers over the course of their day. In longer, more naturalistic recordings, caregivers also tend to use less CDS (REFS Tamis-LeMonda\footnote{That said, Tamis-LeMonda and colleagues found that rank CDS quantity use was highly correlated between short- and long-format recordings.}). The result is greater confidence that the estimated CDS characteristics are representative of what the child typically hears at home.-->


<!--A major contribution of this work is the use of daylong recordings to describe children's language environments. Using a novel combination of a lightweight audio recorder and wearable photo camera, we were able to track children's movements and interactions over the course of a 9--11-hour period in which the experimenter was not present. With long-format recordings of this kind we can make precise descriptive estimates about the speech children hear: typical quantities, variation within a day, and more (REFS: see also Tamis-LeMonda et al....).-->


## How to define temporal contingency for turn taking
Many other studies of child-caregiver turn taking use an arbitrary cut-off for detecting contingency (5 seconds?? Look up references). We base ours on measures of turn taking in interactions with infants and young children. Hilbrink et al. (2015) looked at interaction in a longitudinal corpus from 3 to 18 months and found that infants' responses to mothers began between -700ms and 1200ms relative to the end of the mothers' turns. Complementarily, mothers' responses to infant vocalizations began between -350ms and 650ms relative to the end of the infants' turns. Casillas et al. (2016) investigated the timing of question-answer responses from caregiver to child and from child to caregiver with children between 20 and 35 months. In their study, children's responses typically started between -500ms and 650ms relative to the end of their caregivers' turns. Caregivers' responses typically started between -1000ms and 400ms relative to the end of their children's turns. Because both studies focused on fairly intensive bouts of interaction, and both within WEIRD parental contexts, we defined contingent responses in the current data with slightly generous allowances for overlap and gap: contingent responses must begin with no more than `r allowed.overlap`ms of overlap and `r allowed.gap`ms of gap relative to the offset of the first speaker's turn. We used this same criteria for finding child-to-other turn transitions and other-to-child turn transitions. Transitions were only counted if the other speaker's turn was coded as addressed to 'T' (the target child).

<!--Potentially redefine allowed.overlap and allowed.gap based on ±2.5SD of timing distributions for Hilbrink and Casillas data-->


## Data analysis {#methods-analysisinfo}
<!--We used `r cite_r("r-references.bib")` for all our analyses.-->


# Results {#results}
<!--
- Results:
  - How much speech do children hear overall and what proportion of that is directed to them? How does that compare to other communities we've studied?
    - *measures*: XDS and TDS minutes per hour and proportion (from random selections only)
  - How do ADS and TDS differ?
    - *measures*: utt length, repetitiveness, F0 peaks and ranges, questions, imperatives (?)
  - How much speech do children hear during bouts/bursts of interaction? How often do these bursts occur?
    - *measures*: deltas for m/h TDS, #utts TDS, # TT transitions between random, tt, and va: are they actually different?
    - *measures*: XDS and TDS minutes per hour and proportion (from tt and va selections: do they show similar age effects?)
    - *measures*: sliding window in random to match mean TDS rate/TT transition rates
  - Does interaction influence linguistic practice?
    - *measures*: m/h CHI vocs, # CHI vocs, & voc mat between random, tt, and va
- Discussion
  - Summary of findings
  - When thinking about quantity: Do we care about the avg over the day or do bursts matter more?
    - Benefits of naps between bursts? Natural input cycle? How many 'good' minutes are enough to spur learning on?
  - How should we think about CDS? What is universal about its format?
  - So what is the impact of input in this community? What do we predict?
    - One point often raised: do these kids show a delay? Problematize this.
    - More interesting: language experience itself shapes use of mechanisms for learning, e.g., learning fro overhearing (Shneidman)
  - Big issue we have to face as work continues in this vein: what are these kids learning? We can't continue to pretend that we are capable of defining and encapsulating a phenomenon as emergent as language.
  - Limitations
    - no video data
    - only 10 kids-->
    
## Still to graph
3: sliding window in random to match mean TDS rate/TT transition rates
4: utt length, repetitiveness, F0 peaks and ranges

## SHOULD I ADD DATAPOINTS ON THE UPH FIGS TO SHOW SHNEIDMAN'S DATA?
Age 1:
- US: CDS 616 (SD=231); ADS/OCDS 278 (SD=247)
-- 79% XDS from MOT (~60% XDS MOT is CDS); 8% XDS from children (mostly ADS/OCDS) 
- Mayan: CDS 86 (SD=59); ADS/OCDS 342 (SD=201)
-- 31% XDS from MOT (~4% XDS MOT is CDS); 60% XDS from children (~50% XDS other kids was ADS/OCDS)
Age18mo?:
Age 2:
- US: CDS M=815, SD=376; ADS/OCDS M=411, SD=318
-- M=65%, SD=28% from MOT (directed: M=800, SD=381; overheard: M=211, SD =55);
-- M=7%, SD=10% from kids (directed: M=15, SD=22; overheard: M=86, SD=141)
- Mayan: CDS M=274, SD=166; ADS/OCDS M=271, SD=136
-- M=19%, SD=17% from MOT (directed:M=104, SD=100; overheard:M=82 SD=52);
-- M=61%, SD=27% from kids (directed:M=104, SD=100; overheard:M=82 SD=52)
Age35mo?

###Observation only data
13 months Directed speech 140 (55); Overheard speech 377 (176)
18 months Directed speech 211 (70); Overheard speech 240 (96)
24 months Directed speech 315 (69); Overheard speech 360 (73)
(I think these data weren't coded for adult vs. child speaker)

<!-- is this right?? the values are the same for D vs. O with adult and kid speech: I think it's more like (directed:M=175, SD=100; overheard:M=190 SD=110) according to figure 2-->


```{r prepare_data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Read in annotation files
files <- list.files(path=data.path,pattern="*.txt")
all.data <- data.frame()
for (i in 1:length(files)) {
#  print(files[i])
  newfile <- read_csv(paste0(data.path, files[i]), col_types = cols(val = col_character()))
  newfile$aclew_child_id <- unlist(strsplit(files[i], '\\.'))[1]
  all.data <- rbind(all.data, newfile)
}
all.data$row <- c(1:nrow(all.data))

# Read in supplementary data
ptcp.info <- read_csv(ptcp.info.file, col_types = cols()) %>%
  select(-row)
seg.info <- read_csv(seg.index.file)

# Add participant and segment info
codes <- all.data %>% filter(tier == "code")

all.data <- all.data %>%
  filter(speaker != "") %>%
  left_join(ptcp.info, by = "aclew_child_id") %>%
  mutate(segment = "", sample = "",
         sample_type = "", segment_dur = 0)

for (i in 1:nrow(codes)) {
  rec <- codes$aclew_child_id[i]
  seg <- as.character(codes$val[i])
  seg.on <- codes$start[i]
  seg.off <- codes$stop[i]
  seg.idx <- which(all.data$aclew_child_id == rec &
                     all.data$start < seg.off &
                     all.data$stop > seg.on)
  all.data$segment[seg.idx] <- seg
}

# Label samples
all.data$sample[which(
  grepl('^random', all.data$segment))] <- "random"
all.data$sample[which(
  grepl('tt', all.data$segment))] <- "turn-taking"
all.data$sample[which(
  grepl('va', all.data$segment))] <- "high-activity"

# Label sample types and durations
random.samples <- which(grepl('^random', all.data$segment))
all.data$sample_type[random.samples] <- "random"
all.data$segment_dur[random.samples] <- 5

ext.samples <- which(grepl('^extension', all.data$segment))
all.data$sample_type[ext.samples] <- "extension"
all.data$segment_dur[ext.samples] <- 5

tt.samples <- which(grepl('^tt', all.data$segment))
all.data$sample_type[tt.samples] <- "turn-taking"
all.data$segment_dur[tt.samples] <- 1

va.samples <- which(grepl('^va', all.data$segment))
all.data$sample_type[va.samples] <- "turn-taking"
all.data$segment_dur[va.samples] <- 1
```

```{r XDS_TDS_quantity_random, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Get min/hr speech measures
n.unique.rand.segs <- length(unique(all.data$segment[grepl("random", all.data$segment)]))
n.unique.recs <- length(unique(all.data$aclew_child_id))
all.rand.segments <- tibble(
  aclew_child_id = rep(unique(all.data$aclew_child_id),
                n.unique.rand.segs),
  segment = rep(unique(all.data$segment[grepl("random", all.data$segment)]),
                n.unique.recs))
# XDS
xds.per.seg.rand <- all.data %>%
  filter(sample == "random" & speaker != "CHI" &
           grepl("xds@", tier)) %>%
  group_by(aclew_child_id, segment, segment_dur) %>%
  summarise(xds_min = round(sum(dur)/60000,3)) %>%
  full_join(all.rand.segments, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(segment_dur = 5, xds_min = 0)) %>%
  mutate(xds_mph = (xds_min/segment_dur)*60) %>%
  arrange(aclew_child_id, segment)
# TDS
tds.per.seg.rand <- all.data %>%
  filter(sample == "random" & speaker != "CHI" &
           grepl("xds@", tier) & val == "T") %>%
  group_by(aclew_child_id, segment, segment_dur) %>%
  summarise(tds_min = round(sum(dur)/60000,3)) %>%
  full_join(all.rand.segments, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(segment_dur = 5, tds_min = 0)) %>%
  mutate(tds_mph = (tds_min/segment_dur)*60) %>%
  arrange(aclew_child_id, segment)
# All CDS
cds.per.seg.rand <- all.data %>%
  filter(sample == "random" & speaker != "CHI" &
           grepl("xds@", tier) & (val == "T" | val == "C")) %>%
  group_by(aclew_child_id, segment, segment_dur) %>%
  summarise(cds_min = round(sum(dur)/60000,3)) %>%
  full_join(all.rand.segments, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(segment_dur = 5, cds_min = 0)) %>%
  mutate(cds_mph = (cds_min/segment_dur)*60) %>%
  arrange(aclew_child_id, segment)
# All together
quantity.rand <- xds.per.seg.rand %>%
  full_join(tds.per.seg.rand, by = c("aclew_child_id", "segment", "segment_dur")) %>%
  full_join(cds.per.seg.rand, by = c("aclew_child_id", "segment", "segment_dur")) %>%
  full_join(ptcp.info, by = "aclew_child_id") %>%
  replace_na(list(xds_min = 0, xds_mph = 0,
                  tds_min = 0, tds_mph = 0,
                  cds_min = 0, cds_mph = 0)) %>%
  mutate(prop_tds = tds_min/xds_min)
  # Don't replace NAs with 0s in this case; proportion is not meaningful w/o any speech

# Get xds and tds min/hr by speaker type
all.data$SpkrAge <- "Not known"
all.data$SpkrAge[grepl("FA|MA|UA", all.data$speaker)] <- "Adult"
all.data$SpkrAge[grepl("FC|MC|UC", all.data$speaker)] <- "Child"
all.rand.segments.sa <- tibble(
  aclew_child_id = rep(unique(all.data$aclew_child_id),
                2*n.unique.rand.segs),
  segment = rep(unique(all.data$segment[grepl("random", all.data$segment)]),
                2*n.unique.recs),
  SpkrAge = c(rep("Adult", (n.unique.rand.segs * n.unique.recs)),
              rep("Child", (n.unique.rand.segs * n.unique.recs))))
# XDS
xds.per.seg.rand.sa <- all.data %>%
  filter(sample == "random" & speaker != "CHI" & SpkrAge != "Not known" &
           grepl("xds@", tier)) %>%
  group_by(aclew_child_id, SpkrAge, segment, segment_dur) %>%
  summarise(xds_min.sa = round(sum(dur)/60000,3)) %>%
  full_join(all.rand.segments.sa, by = c("aclew_child_id", "segment", "SpkrAge")) %>%
  replace_na(list(segment_dur = 5, xds_min.sa = 0)) %>%
  mutate(xds_mph.sa = (xds_min.sa/segment_dur)*60) %>%
  arrange(aclew_child_id, segment, SpkrAge)
# TDS
tds.per.seg.rand.sa <- all.data %>%
  filter(sample == "random" & speaker != "CHI" & SpkrAge != "Not known" &
           grepl("xds@", tier) & val == "T") %>%
  group_by(aclew_child_id, SpkrAge, segment, segment_dur) %>%
  summarise(tds_min.sa = round(sum(dur)/60000,3)) %>%
  full_join(all.rand.segments.sa, by = c("aclew_child_id", "segment", "SpkrAge")) %>%
  replace_na(list(segment_dur = 5, tds_min.sa = 0)) %>%
  mutate(tds_mph.sa = (tds_min.sa/segment_dur)*60) %>%
  arrange(aclew_child_id, segment, SpkrAge)
# All CDS
cds.per.seg.rand.sa <- all.data %>%
  filter(sample == "random" & speaker != "CHI" & SpkrAge != "Not known" &
           grepl("xds@", tier) & (val == "T" | val == "C")) %>%
  group_by(aclew_child_id, SpkrAge, segment, segment_dur) %>%
  summarise(cds_min.sa = round(sum(dur)/60000,3)) %>%
  full_join(all.rand.segments.sa, by = c("aclew_child_id", "segment", "SpkrAge")) %>%
  replace_na(list(segment_dur = 5, cds_min.sa = 0)) %>%
  mutate(cds_mph.sa = (cds_min.sa/segment_dur)*60) %>%
  arrange(aclew_child_id, segment, SpkrAge)
# All together
quantity.rand.sa <- xds.per.seg.rand.sa %>%
  full_join(tds.per.seg.rand.sa, by = c("aclew_child_id", "SpkrAge",
                                        "segment", "segment_dur")) %>%
  full_join(cds.per.seg.rand.sa, by = c("aclew_child_id", "SpkrAge",
                                        "segment", "segment_dur")) %>%
  full_join(select(quantity.rand, c("aclew_child_id", "segment", "tds_min")),
            by = c("aclew_child_id", "segment")) %>%
  full_join(ptcp.info, by = "aclew_child_id") %>%
  replace_na(list(xds_min.sa = 0, xds_mph.sa = 0,
                  tds_min.sa = 0, tds_mph.sa = 0,
                  cds_min.sa = 0, cds_mph.sa = 0)) %>%
  mutate(prop_tds.sa = tds_min.sa/xds_min.sa,
         prop_sa.tds = tds_min.sa/tds_min)
  # Don't replace NAs with 0s in this case; proportion is not meaningful w/o any speech
```

```{r plot_XDS_TDS_quantity_random, message=FALSE, warning=FALSE, paged.print=FALSE}
# Graph the basic speech quantity info
# XDS min/hr
xdsmph.segments.rand <- ggplot(quantity.rand,
                          aes(x = age_mo_round, y = xds_mph)) +
  geom_boxplot(aes(group = age_mo_round)) +
  geom_smooth(method = "lm", color = "black") +
  ylab("XDS (min/hr)") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(0,85),
                     breaks=seq(0,85,20)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,85),xlim=c(0,38)) +
  theme_apa()
#xdsmph.segments.rand
# TDS min/hr
tdsmph.segments.rand <- ggplot(quantity.rand,
      aes(x = age_mo_round, y = tds_mph)) +
  geom_boxplot(aes(group = age_mo_round)) +
  geom_smooth(method = "lm", color = "black") +
  ylab("TCDS (min/hr)") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(0,85),
                     breaks=seq(0,85,20)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,85),xlim=c(0,38)) +
  theme_apa()
#tdsmph.segments.rand
tdsmph.segments.rand.zoomedin <- ggplot(quantity.rand,
                                   aes(x = age_mo_round, y = tds_mph)) +
  geom_boxplot(aes(group = age_mo_round)) +
  geom_smooth(method = "lm", color = "black") +
  ylab("TCDS (min/hr)") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(0,40),
                     breaks=seq(0,40,10)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,40),xlim=c(0,38)) +
  theme_apa()
#tdsmph.segments.rand.zoomedin
# TDS prop
tdsprp.segments.rand <- ggplot(quantity.rand,
                          aes(x = age_mo_round, y = prop_tds)) +
  geom_boxplot(aes(group = age_mo_round)) +
  geom_smooth(method = "lm", color = "black") +
  ylab("TCDS/XDS") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(-.2,1.2),
                     breaks=seq(0,1,0.2)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,1),xlim=c(0,38)) +
  theme_apa()
#tdsprp.segments.rand
# prop TDS from adults vs. children
tdsprp.segments.sa.rand <- ggplot(quantity.rand.sa,
                             aes(x = age_mo_round, y = prop_sa.tds,
                                 group = SpkrAge, fill = SpkrAge, color = SpkrAge)) +
  geom_boxplot(aes(group = interaction(age_mo_round, SpkrAge),
                   fill = SpkrAge, color = SpkrAge),
               position = position_dodge(1), alpha = 0.3) +
  geom_smooth(method = "lm") +
  col.sample.bu3 +
  ylab("Prop of TCDS") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(-.2,1.2),
                     breaks=seq(0,1,0.2)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,1), xlim=c(0,38)) +
  theme_apa() + theme(legend.position="none",
                      axis.line = element_line(color="black", size = 0.4))
#tdsprp.segments.sa.rand
# Combine the plots into one
grid.arrange(xdsmph.segments.rand,tdsmph.segments.rand.zoomedin,
             tdsprp.segments.rand, tdsprp.segments.sa.rand, nrow=2, ncol=2)
```

```{r XDS_TDS_quantity_nonrandom, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Get min/hr speech measures
all.nonrand.segments <- seg.info %>%
  filter(!(grepl("random", CodeName))) %>%
  select(aclew_id, CodeName) %>%
  rename(aclew_child_id = aclew_id, segment = CodeName)
all.nonrand.segments$sample <- ifelse(grepl("va", all.nonrand.segments$segment),
                                      "high-activity","turn-taking")
all.nonrand.segments$sample_type <- ifelse(grepl("^va", all.nonrand.segments$segment),
                                      "high-activity", ifelse(
                                        grepl("^tt", all.nonrand.segments$segment),"turn-taking",
                                        "extension"))
# XDS
xds.per.seg.nonrand <- all.data %>%
  filter(sample != "random" & speaker != "CHI" &
           grepl("xds@", tier)) %>%
  group_by(aclew_child_id, segment, segment_dur) %>%
  summarise(xds_min = round(sum(dur)/60000,3)) %>%
  full_join(all.nonrand.segments, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(segment_dur = 1, xds_min = 0)) %>%
  mutate(segment_dur = ifelse(grepl("ext", segment), 5, 1),
         xds_mph = (xds_min/segment_dur)*60) %>%
  arrange(aclew_child_id, segment)
# TDS
tds.per.seg.nonrand <- all.data %>%
  filter(sample != "random" & speaker != "CHI" &
           grepl("xds@", tier) & val == "T") %>%
  group_by(aclew_child_id, segment, segment_dur) %>%
  summarise(tds_min = round(sum(dur)/60000,3)) %>%
  full_join(all.nonrand.segments, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(segment_dur = 1, tds_min = 0)) %>%
  mutate(segment_dur = ifelse(grepl("ext", segment), 5, 1),
         tds_mph = (tds_min/segment_dur)*60) %>%
  arrange(aclew_child_id, segment)
# All CDS
cds.per.seg.nonrand <- all.data %>%
  filter(sample != "random" & speaker != "CHI" &
           grepl("xds@", tier) & (val == "T" | val == "C")) %>%
  group_by(aclew_child_id, segment, segment_dur) %>%
  summarise(cds_min = round(sum(dur)/60000,3)) %>%
  full_join(all.nonrand.segments, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(segment_dur = 1, cds_min = 0)) %>%
  mutate(segment_dur = ifelse(grepl("ext", segment), 5, 1),
         cds_mph = (cds_min/segment_dur)*60) %>%
  arrange(aclew_child_id, segment)
# All together
quantity.nonrand <- xds.per.seg.nonrand %>%
  full_join(tds.per.seg.nonrand, by = c("aclew_child_id", "segment",
                                        "segment_dur", "sample", "sample_type")) %>%
  full_join(cds.per.seg.nonrand, by = c("aclew_child_id", "segment",
                                        "segment_dur", "sample", "sample_type")) %>%
  full_join(ptcp.info, by = "aclew_child_id") %>%
  replace_na(list(xds_min = 0, xds_mph = 0,
                  tds_min = 0, tds_mph = 0,
                  cds_min = 0, cds_mph = 0)) %>%
  mutate(prop_tds = tds_min/xds_min)
  # Don't replace NAs with 0s in this case; proportion is not meaningful w/o any speech

# Get xds and tds min/hr by speaker type
all.nonrand.segments.sa <- tibble(
  aclew_child_id = rep(all.nonrand.segments$aclew_child_id, 2),
  segment = rep(all.nonrand.segments$segment, 2),
  sample = rep(all.nonrand.segments$sample, 2),
  sample_type = rep(all.nonrand.segments$sample_type, 2),
  SpkrAge = c(rep("Adult", nrow(all.nonrand.segments)),
              rep("Child", nrow(all.nonrand.segments))))
# XDS
xds.per.seg.nonrand.sa <- all.data %>%
  filter(sample != "random" & speaker != "CHI" & SpkrAge != "Not known" &
           grepl("xds@", tier)) %>%
  group_by(aclew_child_id, SpkrAge, segment, segment_dur) %>%
  summarise(xds_min.sa = round(sum(dur)/60000,3)) %>%
  full_join(all.nonrand.segments.sa, by = c("aclew_child_id", "segment", "SpkrAge")) %>%
  replace_na(list(segment_dur = 1, xds_min.sa = 0)) %>%
  mutate(segment_dur = ifelse(grepl("ext", segment), 5, 1),
         xds_mph.sa = (xds_min.sa/segment_dur)*60) %>%
  arrange(aclew_child_id, segment, SpkrAge)
# TDS
tds.per.seg.nonrand.sa <- all.data %>%
  filter(sample != "random" & speaker != "CHI" & SpkrAge != "Not known" &
           grepl("xds@", tier) & val == "T") %>%
  group_by(aclew_child_id, SpkrAge, segment, segment_dur) %>%
  summarise(tds_min.sa = round(sum(dur)/60000,3)) %>%
  full_join(all.nonrand.segments.sa, by = c("aclew_child_id", "segment", "SpkrAge")) %>%
  replace_na(list(segment_dur = 1, tds_min.sa = 0)) %>%
  mutate(segment_dur = ifelse(grepl("ext", segment), 5, 1),
         tds_mph.sa = (tds_min.sa/segment_dur)*60) %>%
  arrange(aclew_child_id, segment, SpkrAge)
# All CDS
cds.per.seg.nonrand.sa <- all.data %>%
  filter(sample != "random" & speaker != "CHI" & SpkrAge != "Not known" &
           grepl("xds@", tier) & (val == "T" | val == "C")) %>%
  group_by(aclew_child_id, SpkrAge, segment, segment_dur) %>%
  summarise(cds_min.sa = round(sum(dur)/60000,3)) %>%
  full_join(all.nonrand.segments.sa, by = c("aclew_child_id", "segment", "SpkrAge")) %>%
  replace_na(list(segment_dur = 1, cds_min.sa = 0)) %>%
  mutate(segment_dur = ifelse(grepl("ext", segment), 5, 1),
         cds_mph.sa = (cds_min.sa/segment_dur)*60) %>%
  arrange(aclew_child_id, segment, SpkrAge)
# All together
quantity.nonrand.sa <- xds.per.seg.nonrand.sa %>%
  full_join(tds.per.seg.nonrand.sa, by = c("aclew_child_id", "SpkrAge",
                                           "segment", "segment_dur",
                                           "sample", "sample_type")) %>%
  full_join(cds.per.seg.nonrand.sa, by = c("aclew_child_id", "SpkrAge",
                                           "segment", "segment_dur",
                                           "sample", "sample_type")) %>%
  full_join(select(quantity.nonrand, c("aclew_child_id", "segment", "tds_min")),
            by = c("aclew_child_id", "segment")) %>%
  full_join(ptcp.info, by = "aclew_child_id") %>%
  replace_na(list(xds_min.sa = 0, xds_mph.sa = 0,
                  tds_min.sa = 0, tds_mph.sa = 0,
                  cds_min.sa = 0, cds_mph.sa = 0)) %>%
  mutate(prop_tds.sa = tds_min.sa/xds_min.sa,
         prop_sa.tds = tds_min.sa/tds_min)
  # Don't replace NAs with 0s in this case; proportion is not meaningful w/o any speech
```

```{r plot_XDS_TDS_quantity_nonrandom, message=FALSE, warning=FALSE, paged.print=FALSE}
# Graph the basic speech quantity info
# XDS min/hr
xdsmph.segments.nonrand <- ggplot(quantity.nonrand,
                          aes(x = age_mo_round, y = xds_mph,
                              group = sample, fill = sample, color = sample)) +
  geom_boxplot(aes(group = interaction(age_mo_round, sample),
               fill = sample, color = sample),
               position = position_dodge(1), alpha = 0.3) +
  geom_smooth(aes(lty = sample), method = "lm") +
  scale_fill_manual(values=c("gray60", "gray20")) +
  scale_color_manual(values=c("gray60", "gray20")) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  ylab("XDS (min/hr)") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(0,85),
                     breaks=seq(0,85,20)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,85),xlim=c(0,38)) +
  theme_apa() + theme(legend.position="none",
                      axis.line = element_line(color="black", size = 0.4))
# xdsmph.segments.nonrand
# TDS min/hr
tdsmph.segments.nonrand <- ggplot(quantity.nonrand,
                          aes(x = age_mo_round, y = tds_mph,
                              group = sample, fill = sample, color = sample)) +
  geom_boxplot(aes(group = interaction(age_mo_round, sample),
               fill = sample, color = sample),
               position = position_dodge(1), alpha = 0.3) +
  geom_smooth(aes(lty = sample), method = "lm") +
  scale_fill_manual(values=c("gray60", "gray20")) +
  scale_color_manual(values=c("gray60", "gray20")) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  ylab("TCDS (min/hr)") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(0,85),
                     breaks=seq(0,85,20)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,85),xlim=c(0,38)) +
  theme_apa() + theme(legend.position="none",
                      axis.line = element_line(color="black", size = 0.4))
#tdsmph.segments.nonrand
tdsmph.segments.nonrand.zoomedin <- ggplot(quantity.nonrand,
                          aes(x = age_mo_round, y = tds_mph,
                              group = sample, fill = sample, color = sample)) +
  geom_boxplot(aes(group = interaction(age_mo_round, sample),
               fill = sample, color = sample),
               position = position_dodge(1), alpha = 0.3) +
  geom_smooth(aes(lty = sample), method = "lm") +
  scale_fill_manual(values=c("gray60", "gray20")) +
  scale_color_manual(values=c("gray60", "gray20")) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  ylab("TCDS (min/hr)") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(0,40),
                     breaks=seq(0,40,10)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,40),xlim=c(0,38)) +
  theme_apa() + theme(legend.position="none",
                      axis.line = element_line(color="black", size = 0.4))
#tdsmph.segments.nonrand.zoomedin
# TDS prop
tdsprp.segments.nonrand <- ggplot(quantity.nonrand,
                          aes(x = age_mo_round, y = prop_tds,
                              group = sample, fill = sample, color = sample)) +
  geom_boxplot(aes(group = interaction(age_mo_round, sample),
               fill = sample, color = sample),
               position = position_dodge(1), alpha = 0.3) +
  geom_smooth(aes(lty = sample), method = "lm") +
  scale_fill_manual(values=c("gray60", "gray20")) +
  scale_color_manual(values=c("gray60", "gray20")) +
  scale_linetype_manual(values=c("solid", "dashed")) +
  ylab("TCDS/XDS") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(-.2,1.2),
                     breaks=seq(0,1,0.2)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,1),xlim=c(0,38)) +
  theme_apa() + theme(legend.position="none",
                      axis.line = element_line(color="black", size = 0.4))
#tdsprp.segments.nonrand
# prop TDS from adults vs. children
tdsprp.segments.sa.nonrand <- ggplot(quantity.nonrand.sa,
                             aes(x = age_mo_round, y = prop_sa.tds,
                                 group = SpkrAge, fill = SpkrAge)) +
  geom_boxplot(aes(group = interaction(age_mo_round, SpkrAge, sample),
                  color = interaction(SpkrAge, sample),
                  fill = interaction(SpkrAge, sample)),
               position = position_dodge(3), alpha = 0.3, lwd = 0.2) +
  geom_smooth(aes(group = interaction(SpkrAge, sample),
                  color = interaction(SpkrAge, sample),
                  fill = interaction(SpkrAge, sample),
                  lty = interaction(SpkrAge, sample)),
              method = "lm", alpha = 0.2) +
  scale_fill_manual(values=c(viridis(3)[1], viridis(3)[2],
                             viridis(3)[1], viridis(3)[2])) +
  scale_color_manual(values=c(viridis(3)[1], viridis(3)[2],
                             viridis(3)[1], viridis(3)[2])) +
  scale_linetype_manual(values=c("solid", "solid", "dashed", "dashed")) +
  ylab("Prop of TCDS") + xlab("Child age (mo)")	+
  scale_y_continuous(limits=c(-.2,1.2),
                     breaks=seq(0,1,0.2)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,1), xlim=c(0,38)) +
  theme_apa() + theme(legend.position="none",
                      axis.line = element_line(color="black", size = 0.4))
#tdsprp.segments.sa.nonrand
# Combine the plots into one
grid.arrange(xdsmph.segments.nonrand, tdsmph.segments.nonrand.zoomedin,
             tdsprp.segments.nonrand, tdsprp.segments.sa.nonrand, nrow=2, ncol=2)
```

``` {r chi_voctypes_overall}
chi.vm.lx.utts <- all.data %>%
  filter((tier == "vcm@CHI" | tier == "lex@CHI" | tier == "mwu@CHI")) %>%
  mutate(voc.rating = ifelse(val == "M", 4,
                             ifelse((val == "1" | val == "W"), 3,
                                    ifelse((val == "0" | val == "C"), 2,
                                           ifelse(val == "N", 1, 0))))) %>%
  filter(voc.rating > 0) %>%
  group_by(aclew_child_id, segment, sample, start) %>%
  summarise(max_voc.rtg = max(voc.rating))

all.voc.types.per.child <- tibble(
  aclew_child_id = rep(ptcp.info$aclew_child_id, 4),
  max_voc.rtg = c(rep(1, length(ptcp.info$aclew_child_id)), rep(2, length(ptcp.info$aclew_child_id)),
                  rep(3, length(ptcp.info$aclew_child_id)), rep(4, length(ptcp.info$aclew_child_id)))
)

chi.nvocs <- chi.vm.lx.utts %>%
  group_by(aclew_child_id) %>%
  summarise(n_vocs = n())

chi.vm.lx.voc.type.props <- chi.vm.lx.utts %>%
  group_by(aclew_child_id, max_voc.rtg) %>%
  summarise(n_voc.type = n()) %>%
  full_join(all.voc.types.per.child, by = c("aclew_child_id", "max_voc.rtg")) %>%
  replace_na(list(n_voc.type = 0)) %>%
  full_join(chi.nvocs, by = "aclew_child_id") %>%
  mutate(prop_voc.type = round(n_voc.type/n_vocs, 3)) %>%
  arrange(aclew_child_id, max_voc.rtg) %>%
  full_join(ptcp.info, by = "aclew_child_id")
```

``` {r plot_chi_voctypes_overall}
chi.vm.lx.voc.type.props <- chi.vm.lx.voc.type.props %>%
  mutate(voc.type = factor(as.factor(max_voc.rtg), labels = c("NCB", "CB", "SW", "MW")))
voc.mat.by.age <- ggplot(
  data = chi.vm.lx.voc.type.props,
  aes(x = age_mo_round, y = prop_voc.type, group = as.factor(voc.type))) +
  geom_point(aes(color = as.factor(voc.type))) +
  geom_smooth(aes(color = as.factor(voc.type), fill = as.factor(voc.type)), method = "loess") +
  ylab("Prop of linguistic vocs") + xlab("Child age (mo)") +
  labs(fill='Voc type') +
  labs(color='Voc type') +
  scale_y_continuous(limits=c(-0.5,1.5),
                     breaks=seq(0,1,0.2)) +
  scale_x_continuous(limits=c(0,38),
                     breaks=seq(0,38,6)) +
  coord_cartesian(ylim=c(0,1), xlim=c(0,38)) +
  theme_apa() + theme(
    legend.position = c(0.9, 0.85),
    legend.background = element_rect(fill="transparent"),
    axis.line = element_line(color="black", size = 0.4))
voc.mat.by.age
```

``` {r sample_differences}
# deltas m/h XDS, TDS, and CDS mph
quantity.mph.per.sample <- quantity.rand %>%
  mutate(sample = "random",
         sample_type = "random") %>%
  bind_rows(quantity.nonrand) %>%
  group_by(aclew_child_id, sample) %>%
  summarise(m_xds_mph = mean(xds_mph),
         m_tds_mph = mean(tds_mph),
         m_cds_mph = mean(cds_mph))
deltas.random.v.tt <- quantity.mph.per.sample %>%
  filter(sample != "high-activity") %>%
  arrange(aclew_child_id, sample) %>%
  mutate(d_xds_mph = 0,
         d_tds_mph = 0,
         d_cds_mph = 0)
for (i in 2:nrow(deltas.random.v.tt)) {
  deltas.random.v.tt$d_xds_mph[i] <-
    deltas.random.v.tt$m_xds_mph[i] -
    deltas.random.v.tt$m_xds_mph[i-1] # set up for tt - random
  deltas.random.v.tt$d_tds_mph[i] <-
    deltas.random.v.tt$m_tds_mph[i] - deltas.random.v.tt$m_tds_mph[i-1]
  deltas.random.v.tt$d_cds_mph[i] <-
    deltas.random.v.tt$m_cds_mph[i] - deltas.random.v.tt$m_cds_mph[i-1]
}
deltas.random.v.tt <- deltas.random.v.tt %>%
  filter(sample != "random") %>% # only keep meaningful vals
  select(aclew_child_id, d_xds_mph, d_tds_mph, d_cds_mph) %>%
  mutate(delta = "tt-random")
deltas.random.v.va <- quantity.mph.per.sample %>%
  filter(sample != "turn-taking") %>%
  arrange(aclew_child_id, sample) %>%
  mutate(d_xds_mph = 0,
         d_tds_mph = 0,
         d_cds_mph = 0)
for (i in 2:nrow(deltas.random.v.va)) {
  deltas.random.v.va$d_xds_mph[i] <-
    deltas.random.v.va$m_xds_mph[i-1] -
    deltas.random.v.va$m_xds_mph[i] # set up for va - random
  deltas.random.v.va$d_tds_mph[i] <-
    deltas.random.v.va$m_tds_mph[i-1] - deltas.random.v.va$m_tds_mph[i]
  deltas.random.v.va$d_cds_mph[i] <-
    deltas.random.v.va$m_cds_mph[i-1] - deltas.random.v.va$m_cds_mph[i]
}
deltas.random.v.va <- deltas.random.v.va %>%
  filter(sample == "random") %>% # only keep meaningful vals
  select(aclew_child_id, d_xds_mph, d_tds_mph, d_cds_mph) %>%
  mutate(delta = "va-random")
deltas.random.v.oth <- bind_rows(deltas.random.v.tt, deltas.random.v.va) %>%
  full_join(ptcp.info, by = "aclew_child_id")

# deltas utt/h XDS, TDS, and CDS
tot.dur.samples.per.rec <- seg.info %>%
  mutate(duration = ifelse(grepl('1min', Sample), 1, 5),
         sample = ifelse(grepl('random', CodeName), "random",
                         ifelse(grepl('va', CodeName), "high-activity",
                                "turn-taking"))) %>%
  select(aclew_id, CodeName, duration, sample) %>%
  rename(aclew_child_id = aclew_id, segment = CodeName)
n.utts.per.sample.all <- all.data %>%
  filter(speaker != "CHI" & grepl("xds@", tier)) %>%
  group_by(aclew_child_id, segment, val) %>%
  summarise(n_utts = n()) %>%
  full_join(tot.dur.samples.per.rec, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(val = "T", n_utts = 0))
n.utts.per.sample.xds <- n.utts.per.sample.all %>%
  group_by(aclew_child_id, segment, sample, duration) %>%
  summarise(n_utts_seg = sum(n_utts)) %>%
  mutate(xds_uph = (n_utts_seg/duration)*60) %>%
  group_by(aclew_child_id, sample) %>%
  summarise(m_xds_uph = mean(xds_uph))
n.utts.per.sample.tds <- n.utts.per.sample.all %>%
  filter(val == "T") %>%
  group_by(aclew_child_id, segment, sample, duration) %>%
  summarise(n_utts_seg = sum(n_utts)) %>%
  mutate(tds_uph = (n_utts_seg/duration)*60) %>%
  group_by(aclew_child_id, sample) %>%
  summarise(m_tds_uph = mean(tds_uph))
n.utts.per.sample.cds <- n.utts.per.sample.all %>%
  filter(val == "T" | val == "C") %>%
  group_by(aclew_child_id, segment, sample, duration) %>%
  summarise(n_utts_seg = sum(n_utts)) %>%
  mutate(cds_uph = (n_utts_seg/duration)*60) %>%
  group_by(aclew_child_id, sample) %>%
  summarise(m_cds_uph = mean(cds_uph))
uph.per.sample <- n.utts.per.sample.xds %>%
  full_join(n.utts.per.sample.tds, by = c("aclew_child_id", "sample")) %>%
  full_join(n.utts.per.sample.cds, by = c("aclew_child_id", "sample"))
deltas.random.v.tt.uph <- uph.per.sample %>%
  filter(sample != "high-activity") %>%
  mutate(d_xds_uph = 0,
         d_tds_uph = 0,
         d_cds_uph = 0) %>%
  arrange(aclew_child_id, sample)
for (i in 2:nrow(deltas.random.v.tt.uph)) {
  deltas.random.v.tt.uph$d_xds_uph[i] <-
    deltas.random.v.tt.uph$m_xds_uph[i] - deltas.random.v.tt.uph$m_xds_uph[i-1]
  deltas.random.v.tt.uph$d_tds_uph[i] <-
    deltas.random.v.tt.uph$m_tds_uph[i] - deltas.random.v.tt.uph$m_tds_uph[i-1]
  deltas.random.v.tt.uph$d_cds_uph[i] <-
    deltas.random.v.tt.uph$m_cds_uph[i] - deltas.random.v.tt.uph$m_cds_uph[i-1]
}
deltas.random.v.tt.uph <- deltas.random.v.tt.uph %>%
  filter(sample != "random") %>%
  select(aclew_child_id, d_xds_uph, d_tds_uph, d_cds_uph) %>%
  mutate(delta = "tt-random")
deltas.random.v.va.uph <- uph.per.sample %>%
  filter(sample != "turn-taking") %>%
  mutate(d_xds_uph = 0,
         d_tds_uph = 0,
         d_cds_uph = 0) %>%
  arrange(aclew_child_id, sample)
for (i in 2:nrow(deltas.random.v.va.uph)) {
  deltas.random.v.va.uph$d_xds_uph[i] <-
    deltas.random.v.va.uph$m_xds_uph[i-1] - deltas.random.v.va.uph$m_xds_uph[i]
  deltas.random.v.va.uph$d_tds_uph[i] <-
    deltas.random.v.va.uph$m_tds_uph[i-1] - deltas.random.v.va.uph$m_tds_uph[i]
  deltas.random.v.va.uph$d_cds_uph[i] <-
    deltas.random.v.va.uph$m_cds_uph[i-1] - deltas.random.v.va.uph$m_cds_uph[i]
}
deltas.random.v.va.uph <- deltas.random.v.va.uph %>%
  filter(sample == "random") %>%
  select(aclew_child_id, d_xds_uph, d_tds_uph, d_cds_uph) %>%
  mutate(delta = "va-random")
deltas.random.v.oth.utts <- bind_rows(deltas.random.v.tt.uph, deltas.random.v.va.uph) %>%
  full_join(ptcp.info, by = "aclew_child_id")

# TT transitions
all.segments <- all.rand.segments %>%
  mutate(sample = "random", sample_type = "random") %>%
  bind_rows(all.nonrand.segments) %>%
  arrange(aclew_child_id, segment)
turn.transitions <- tibble(
  aclew_child_id = NA,
  segment = NA,
  tier = NA,
  speaker = NA,
  start = NA,
  stop = NA,
  tm1.tier = NA,
  tm1.speaker = NA,
  tm1.start = NA,
  tm1.stop = NA,
  tm1.val = NA,
  tp1.tier = NA,
  tp1.speaker = NA,
  tp1.start = NA,
  tp1.stop = NA,
  tp1.val = NA
)
for (i in 1:nrow(all.segments)) {
  subdata <- all.data %>%
    filter(aclew_child_id == all.segments$aclew_child_id[i] &
             segment == all.segments$segment[i])
  c_utt <- subdata %>%
    filter(tier == "CHI")
  used.tm1s <- c()
  used.tp1s <- c()
  child <- all.segments$aclew_child_id[i]
  # Save turn-by-turn info
  chi.turn.info <- c_utt %>%
    select(aclew_child_id, segment, tier, speaker, start, stop) %>%
    mutate(tm1.tier = NA, tm1.speaker = NA, tm1.start = NA, tm1.stop = NA, tm1.val = NA,
           tp1.tier = NA, tp1.speaker = NA, tp1.start = NA, tp1.stop = NA, tp1.val = NA)
  for (j in 1:nrow(c_utt)) {
    # Find CHI-OTH transitions
    tp1.start <- c_utt$stop[j] - allowed.overlap
    tp1.stop <- tp1.start + allowed.overlap + allowed.gap
    t.plus1 <- which(subdata$speaker != "CHI" &
                    (subdata$val == "T"|subdata$val == "C") &
                    subdata$start >= tp1.start &
                    subdata$start <= tp1.stop)
   # Find OTH-CHI transitions
    tm1.start <- c_utt$start[j] - allowed.gap
    tm1.stop <- tm1.start + allowed.gap + allowed.overlap
    t.minus1 <- which(subdata$speaker != "CHI" &
                    (subdata$val == "T"|subdata$val == "C") &
                    subdata$stop <= tm1.stop &
                    subdata$stop >= tm1.start)
    if(length(t.plus1) > 0) {
      tp1.match <- 0
      for (turn in t.plus1) {
        if (!(turn %in% used.tp1s) & tp1.match == 0) {
          used.tp1s <- c(used.tp1s, turn)
          chi.turn.info$tp1.tier[j] <- subdata$tier[turn]
          chi.turn.info$tp1.speaker[j] <- subdata$speaker[turn]
          chi.turn.info$tp1.start[j] <- subdata$start[turn]
          chi.turn.info$tp1.stop[j] <- subdata$stop[turn]
          chi.turn.info$tp1.val[j] <- subdata$val[turn]
          tp1.match <- 1
        }
      }
    }
    if(length(t.minus1) > 0) {
      tm1.match <- 0
      for (turn in t.minus1) {
        if (!(turn %in% used.tm1s) & tm1.match == 0) {
          used.tm1s <- c(used.tm1s, turn)
          chi.turn.info$tm1.tier[j] <- subdata$tier[turn]
          chi.turn.info$tm1.speaker[j] <- subdata$speaker[turn]
          chi.turn.info$tm1.start[j] <- subdata$start[turn]
          chi.turn.info$tm1.stop[j] <- subdata$stop[turn]
          chi.turn.info$tm1.val[j] <- subdata$val[turn]
          tm1.match <- 1
        }
      }
    }
  }
  turn.transitions <- bind_rows(turn.transitions, chi.turn.info)
}
turn.transitions <- turn.transitions %>%
  filter(!(is.na(tier)))
turn.transitions.overview.o_c <- turn.transitions %>%
  group_by(aclew_child_id, segment, tm1.val) %>%
  summarise(n.o_c.tts = n()) %>%
  rename(oth.spkr = tm1.val) %>%
  replace_na(list(oth.spkr = "O"))
turn.transitions.overview.c_o <- turn.transitions %>%
  group_by(aclew_child_id, segment, tp1.val) %>%
  summarise(n.c_o.tts = n()) %>%
  rename(oth.spkr = tp1.val) %>%
  replace_na(list(oth.spkr = "O"))
all.tt.combos <-  all.segments %>%
  rbind(all.segments) %>%
  rbind(all.segments) %>%
  mutate(oth.spkr = c(rep("T", nrow(all.segments)),
                      rep("C", nrow(all.segments)),
                      rep("O", nrow(all.segments))),
         duration = ifelse(grepl('extension', sample_type), 5,
                           ifelse(grepl('random', sample_type), 5, 1))) %>%
  arrange(aclew_child_id, segment, oth.spkr) %>%
  full_join(turn.transitions.overview.o_c,
            by = c("aclew_child_id", "segment", "oth.spkr")) %>%
  full_join(turn.transitions.overview.c_o,
            by = c("aclew_child_id", "segment", "oth.spkr")) %>%
  replace_na(list(n.o_c.tts = 0, n.c_o.tts = 0)) %>%
  arrange(aclew_child_id, segment, oth.spkr)
tth.per.sample.tds <- all.tt.combos %>%
  filter(oth.spkr == "T") %>%
  group_by(aclew_child_id, sample) %>%
  summarise(dur.sample = sum(duration),
            S.o_c.tth.tds = sum(n.o_c.tts),
            S.c_o.tth.tds = sum(n.c_o.tts)) %>%
  mutate(o_c.tth.tds = (S.o_c.tth.tds/dur.sample)*60,
         c_o.tth.tds = (S.c_o.tth.tds/dur.sample)*60)
tth.per.sample.cds <- all.tt.combos %>%
  filter(oth.spkr == "T" | oth.spkr == "C") %>%
  group_by(aclew_child_id, segment, sample, duration) %>%
  summarise(n_o_c.tts.TC = sum(n.o_c.tts),
            n_c_o.tts.TC = sum(n.c_o.tts)) %>%
  ungroup() %>%
  group_by(aclew_child_id, sample) %>%
  summarise(dur.sample = sum(duration),
            S.o_c.tth.cds = sum(n_o_c.tts.TC),
            S.c_o.tth.cds = sum(n_c_o.tts.TC)) %>%
  mutate(o_c.tth.cds = (S.o_c.tth.cds/dur.sample)*60,
         c_o.tth.cds = (S.c_o.tth.cds/dur.sample)*60)
tth.per.sample <- tth.per.sample.tds %>%
  select(-dur.sample) %>%
  full_join(tth.per.sample.cds, by = c("aclew_child_id", "sample")) %>%
  arrange(aclew_child_id, sample) %>%
  mutate(d_o_c.tth.tds = 0,
         d_c_o.tth.tds = 0,
         d_o_c.tth.cds = 0,
         d_c_o.tth.cds = 0)
deltas.random.v.tt.tth <- tth.per.sample %>%
  filter(sample != "high-activity")
for (i in 2:nrow(deltas.random.v.tt.tth)) {
  deltas.random.v.tt.tth$d_o_c.tth.tds[i] <-
    deltas.random.v.tt.tth$o_c.tth.tds[i] -
    deltas.random.v.tt.tth$o_c.tth.tds[i-1] # set up for tt - random
  deltas.random.v.tt.tth$d_c_o.tth.tds[i] <-
    deltas.random.v.tt.tth$c_o.tth.tds[i] - deltas.random.v.tt.tth$c_o.tth.tds[i-1]
  deltas.random.v.tt.tth$d_o_c.tth.cds[i] <-
    deltas.random.v.tt.tth$o_c.tth.cds[i] -
    deltas.random.v.tt.tth$o_c.tth.cds[i-1]
  deltas.random.v.tt.tth$d_c_o.tth.cds[i] <-
    deltas.random.v.tt.tth$c_o.tth.cds[i] - deltas.random.v.tt.tth$c_o.tth.cds[i-1]
}
deltas.random.v.tt.tth <- deltas.random.v.tt.tth %>%
  filter(sample != "random") %>% # only keep meaningful vals
  ungroup() %>%
  select(aclew_child_id, d_o_c.tth.tds, d_c_o.tth.tds, d_o_c.tth.cds, d_c_o.tth.cds) %>%
  mutate(delta = "tt-random")
deltas.random.v.ha.tth <- tth.per.sample %>%
  filter(sample != "turn-taking")
for (i in 2:nrow(deltas.random.v.ha.tth)) {
  deltas.random.v.ha.tth$d_o_c.tth.tds[i] <-
    deltas.random.v.ha.tth$o_c.tth.tds[i-1] -
    deltas.random.v.ha.tth$o_c.tth.tds[i] # set up for ha - random
  deltas.random.v.ha.tth$d_c_o.tth.tds[i] <-
    deltas.random.v.ha.tth$c_o.tth.tds[i-1] - deltas.random.v.ha.tth$c_o.tth.tds[i]
  deltas.random.v.ha.tth$d_o_c.tth.cds[i] <-
    deltas.random.v.ha.tth$o_c.tth.cds[i-1] -
    deltas.random.v.ha.tth$o_c.tth.cds[i]
  deltas.random.v.ha.tth$d_c_o.tth.cds[i] <-
    deltas.random.v.ha.tth$c_o.tth.cds[i-1] - deltas.random.v.ha.tth$c_o.tth.cds[i]
}
deltas.random.v.ha.tth <- deltas.random.v.ha.tth %>%
  filter(sample == "random") %>% # only keep meaningful vals
  ungroup() %>%
  select(aclew_child_id, d_o_c.tth.tds, d_c_o.tth.tds, d_o_c.tth.cds, d_c_o.tth.cds) %>%
  mutate(delta = "va-random")
deltas.random.v.oth.tth <- deltas.random.v.tt.tth %>%
  bind_rows(deltas.random.v.ha.tth) %>%
  full_join(ptcp.info, by = "aclew_child_id")

# CHIVOC mph and uph
chi.voc <- all.data %>%
  filter(tier == "CHI") %>%
  group_by(aclew_child_id, segment) %>%
  summarise(n_utts = n(),
            dur.utts = round(sum(dur)/60000,3)) %>%
  full_join(all.segments, by = c("aclew_child_id", "segment")) %>%
  replace_na(list(n_utts = 0, dur.utts = 0)) %>%
  mutate(duration = ifelse(grepl('extension', segment), 5,
                                 ifelse(grepl('random', segment), 5, 1)))
chi.voc.per.sample <- chi.voc %>%
  group_by(aclew_child_id, sample) %>%
  summarise(S_n_utts = sum(n_utts),
            S_dur.utts = sum(dur.utts),
            S_duration = sum(duration)) %>%
  mutate(cvc_uph = (S_n_utts/S_duration)*60,
         cvc_mph = (S_dur.utts/S_duration)*60) %>%
  select(-S_n_utts, -S_dur.utts, -S_duration) %>%
  arrange(aclew_child_id, sample) %>%
  mutate(d_cvc_uph = 0,
         d_cvc_mph = 0)
deltas.random.v.tt.cvc <- chi.voc.per.sample %>%
  filter(sample != "high-activity")
for (i in 2:nrow(deltas.random.v.tt.cvc)) {
  deltas.random.v.tt.cvc$d_cvc_uph[i] <-
    deltas.random.v.tt.cvc$cvc_uph[i] -
    deltas.random.v.tt.cvc$cvc_uph[i-1] # set up for tt - random
  deltas.random.v.tt.cvc$d_cvc_mph[i] <-
    deltas.random.v.tt.cvc$cvc_mph[i] - deltas.random.v.tt.cvc$cvc_mph[i-1]
}
deltas.random.v.tt.cvc <- deltas.random.v.tt.cvc %>%
  filter(sample != "random") %>% # only keep meaningful vals
  ungroup() %>%
  select(aclew_child_id, d_cvc_uph, d_cvc_mph) %>%
  mutate(delta = "tt-random")
deltas.random.v.ha.cvc <- chi.voc.per.sample %>%
  filter(sample != "turn-taking")
for (i in 2:nrow(deltas.random.v.ha.cvc)) {
  deltas.random.v.ha.cvc$d_cvc_uph[i] <-
    deltas.random.v.ha.cvc$cvc_uph[i-1] -
    deltas.random.v.ha.cvc$cvc_uph[i] # set up for ha - random
  deltas.random.v.ha.cvc$d_cvc_mph[i] <-
    deltas.random.v.ha.cvc$cvc_mph[i-1] - deltas.random.v.ha.cvc$cvc_mph[i]
}
deltas.random.v.ha.cvc <- deltas.random.v.ha.cvc %>%
  filter(sample == "random") %>% # only keep meaningful vals
  ungroup() %>%
  select(aclew_child_id, d_cvc_uph, d_cvc_mph) %>%
  mutate(delta = "va-random")
deltas.random.v.oth.cvc <- deltas.random.v.tt.cvc %>%
  bind_rows(deltas.random.v.ha.cvc) %>%
  full_join(ptcp.info, by = "aclew_child_id")

# CHIVM
chi.vm.lx.per.segment <- chi.vm.lx.utts %>%
  group_by(aclew_child_id, sample, segment) %>%
  summarise(n_vocs = n(),
            m_voc.rtg = mean(max_voc.rtg),
            md_voc.rtg = median(max_voc.rtg),
            sd_voc.rtg = sd(max_voc.rtg)) %>%
  full_join(ptcp.info, by = c("aclew_child_id"))
chi.vm.lx.per.sample <- chi.vm.lx.per.segment %>%
  group_by(aclew_child_id, sample) %>%
  summarise(voc_rtg = mean(m_voc.rtg)) %>%
  arrange(aclew_child_id, sample) %>%
  mutate(d_voc_rtg = 0)
deltas.random.v.tt.vrt <- chi.vm.lx.per.sample %>%
  filter(sample != "high-activity")
for (i in 2:nrow(deltas.random.v.tt.vrt)) {
  deltas.random.v.tt.vrt$d_voc_rtg[i] <-
    deltas.random.v.tt.vrt$voc_rtg[i] -
    deltas.random.v.tt.vrt$voc_rtg[i-1] # set up for tt - random
}
deltas.random.v.tt.vrt <- deltas.random.v.tt.vrt %>%
  filter(sample != "random") %>% # only keep meaningful vals
  ungroup() %>%
  select(aclew_child_id, d_voc_rtg) %>%
  mutate(delta = "tt-random")
deltas.random.v.ha.vrt <- chi.vm.lx.per.sample %>%
  filter(sample != "turn-taking")
for (i in 2:nrow(deltas.random.v.ha.vrt)) {
  deltas.random.v.ha.vrt$d_voc_rtg[i] <-
    deltas.random.v.ha.vrt$voc_rtg[i-1] -
    deltas.random.v.ha.vrt$voc_rtg[i] # set up for ha - random
}
deltas.random.v.ha.vrt <- deltas.random.v.ha.vrt %>%
  filter(sample == "random") %>% # only keep meaningful vals
  ungroup() %>%
  select(aclew_child_id, d_voc_rtg) %>%
  mutate(delta = "va-random")
deltas.random.v.oth.vrt <- deltas.random.v.tt.vrt %>%
  bind_rows(deltas.random.v.ha.vrt) %>%
  full_join(ptcp.info, by = "aclew_child_id")
```

``` {r plot_sample_differences, message=FALSE, warning=FALSE, paged.print=FALSE}
# XDS/TDS/CDS mph and uph
# mph: deltas.random.v.oth
# uph: deltas.random.v.oth.utts
deltas.random.v.oth.input <- deltas.random.v.oth %>%
  full_join(select(deltas.random.v.oth.utts, aclew_child_id,
                   delta, d_xds_uph, d_tds_uph, d_cds_uph),
            by = c("aclew_child_id", "delta"))

# TDS MPH: Delta TDS mph between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.input %>%
              group_by(delta) %>%
              summarise(m = mean(d_tds_mph)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.input %>%
           group_by(delta) %>%
           summarise(se = sem(d_tds_mph)) %>%
           select(se))[[1]]
)
delta.tds.mph.plot <- ggplot(
  data = deltas.random.v.oth.input, aes(x = delta, y = d_tds_mph)) +
  geom_violin(data = deltas.random.v.oth.input, aes(x = delta, y = d_tds_mph)) +
  geom_jitter(data = deltas.random.v.oth.input, aes(x = delta, y = d_tds_mph),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                    width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"TCDS (min/hr)"))) +
  ylim(c(-30,20)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

# XDS MPH: Delta XDS mph between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.input %>%
              group_by(delta) %>%
              summarise(m = mean(d_xds_mph)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.input %>%
           group_by(delta) %>%
           summarise(se = sem(d_xds_mph)) %>%
           select(se))[[1]]
)
delta.xds.mph.plot <- ggplot(
  data = deltas.random.v.oth.input, aes(x = delta, y = d_xds_mph)) +
  geom_violin(data = deltas.random.v.oth.input, aes(x = delta, y = d_xds_mph)) +
  geom_jitter(data = deltas.random.v.oth.input, aes(x = delta, y = d_xds_mph),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                    width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"XDS (min/hr)"))) +
  ylim(c(-30,20)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

# TDS UPH: Delta TDS uph between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.input %>%
              group_by(delta) %>%
              summarise(m = mean(d_tds_uph)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.input %>%
           group_by(delta) %>%
           summarise(se = sem(d_tds_uph)) %>%
           select(se))[[1]]
)
delta.tds.uph.plot <- ggplot(
  data = deltas.random.v.oth.input, aes(x = delta, y = d_tds_uph)) +
  geom_violin(data = deltas.random.v.oth.input, aes(x = delta, y = d_tds_uph)) +
  geom_jitter(data = deltas.random.v.oth.input, aes(x = delta, y = d_tds_uph),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                    width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"TCDS (utt/hr)"))) +
  ylim(c(-700,1000)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

# XDS UPH: Delta XDS uph between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.input %>%
              group_by(delta) %>%
              summarise(m = mean(d_xds_uph)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.input %>%
           group_by(delta) %>%
           summarise(se = sem(d_xds_uph)) %>%
           select(se))[[1]]
)
delta.xds.uph.plot <- ggplot(
  data = deltas.random.v.oth.input, aes(x = delta, y = d_xds_uph)) +
  geom_violin(data = deltas.random.v.oth.input, aes(x = delta, y = d_xds_uph)) +
  geom_jitter(data = deltas.random.v.oth.input, aes(x = delta, y = d_xds_uph),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                    width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"XDS (utt/hr)"))) +
  ylim(c(-700,1000)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

grid.arrange(delta.tds.mph.plot,delta.xds.mph.plot,
             delta.tds.uph.plot,delta.xds.uph.plot, nrow=2, ncol=2)


# CHI VOC: Delta voc mph between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.cvc %>%
              group_by(delta) %>%
              summarise(m = mean(d_cvc_mph)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.cvc %>%
           group_by(delta) %>%
           summarise(se = sem(d_cvc_mph)) %>%
           select(se))[[1]]
)
delta.cvc.mph.plot <- ggplot(
  data = deltas.random.v.oth.cvc, aes(x = delta, y = d_cvc_mph)) +
  geom_violin(data = deltas.random.v.oth.cvc, aes(x = delta, y = d_cvc_mph)) +
  geom_jitter(data = deltas.random.v.oth.cvc, aes(x = delta, y = d_cvc_mph),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"CHI voc (min/hr)"))) +
  ylim(c(-10,20)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

# CHI VOC: Delta voc uph between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.cvc %>%
              group_by(delta) %>%
              summarise(m = mean(d_cvc_uph)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.cvc %>%
           group_by(delta) %>%
           summarise(se = sem(d_cvc_uph)) %>%
           select(se))[[1]]
)
delta.cvc.uph.plot <- ggplot(
  data = deltas.random.v.oth.cvc, aes(x = delta, y = d_cvc_uph)) +
  geom_violin(data = deltas.random.v.oth.cvc, aes(x = delta, y = d_cvc_uph)) +
  geom_jitter(data = deltas.random.v.oth.cvc, aes(x = delta, y = d_cvc_uph),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"CHI voc (utt/hr)"))) +
  ylim(c(-100,2000)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

# CHI VOCMAT: Delta voc mat rating between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.vrt %>%
              group_by(delta) %>%
              summarise(m = mean(d_voc_rtg)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.vrt %>%
           group_by(delta) %>%
           summarise(se = sem(d_voc_rtg)) %>%
           select(se))[[1]]
)
delta.voc.rtg.plot <- ggplot(
  data = deltas.random.v.oth.vrt, aes(x = delta, y = d_voc_rtg)) +
  geom_violin(data = deltas.random.v.oth.vrt, aes(x = delta, y = d_voc_rtg)) +
  geom_jitter(data = deltas.random.v.oth.vrt, aes(x = delta, y = d_voc_rtg),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"CHI voc mat (1-4)"))) +
  ylim(c(-.2,0.6)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

# TDS/CDS ttph: Delta O->C transitions between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.tth %>%
              group_by(delta) %>%
              summarise(m = mean(d_o_c.tth.tds)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.tth %>%
           group_by(delta) %>%
           summarise(se = sem(d_o_c.tth.tds)) %>%
           select(se))[[1]]
)
delta.tds.tth.o_c.plot <- ggplot(
  data = deltas.random.v.oth.tth, aes(x = delta, y = d_o_c.tth.tds)) +
  geom_violin(data = deltas.random.v.oth.tth, aes(x = delta, y = d_o_c.tth.tds)) +
  geom_jitter(data = deltas.random.v.oth.tth, aes(x = delta, y = d_o_c.tth.tds),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"OTH-TCHI (tt/hr)"))) +
  ylim(c(-100,600)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

# TDS/CDS ttph: Delta C->O transitions between samples
mse.info <- tibble(
  delta = c("tt-random", "va-random"),
  means = c(deltas.random.v.oth.tth %>%
              group_by(delta) %>%
              summarise(m = mean(d_c_o.tth.tds)) %>%
              select(m))[[1]],
  se = c(deltas.random.v.oth.tth %>%
           group_by(delta) %>%
           summarise(se = sem(d_c_o.tth.tds)) %>%
           select(se))[[1]]
)
delta.tds.tth.c_o.plot <- ggplot(
  data = deltas.random.v.oth.tth, aes(x = delta, y = d_c_o.tth.tds)) +
  geom_violin(data = deltas.random.v.oth.tth, aes(x = delta, y = d_c_o.tth.tds)) +
  geom_jitter(data = deltas.random.v.oth.tth, aes(x = delta, y = d_c_o.tth.tds),
              shape = 1, width = .1, size = 1) +
  geom_errorbar(data = mse.info,
                aes(y = means, ymax = means + (1.96 * se), ymin = means + (-1.96 * se)),
                    width = 0.25) +
  geom_point(data = mse.info, aes(y = means), size = 2) +
  geom_hline(yintercept = 0, lty = "dashed") +
  ylab(expression(paste(Delta,"TCHI-OTH (tt/hr)"))) +
  ylim(c(-100,600)) +
  xlab("Samples compared") +
  scale_x_discrete(labels = c('TT - R','VA - R')) +
  theme_apa() +
  theme(axis.title.x = element_text(size=9),
	axis.title.y = element_text(size=9))

grid.arrange(delta.cvc.mph.plot,delta.voc.rtg.plot,
             delta.tds.tth.o_c.plot, delta.tds.tth.c_o.plot, nrow=2, ncol=2)

```

``` {r prevalence_tt_estimate}
best.min.avgs <- tth.per.sample %>%
  filter(sample != "random") %>%
  select(-d_c_o.tth.cds, -d_c_o.tth.tds, -d_o_c.tth.cds, -d_o_c.tth.tds)

```

# Discussion {#disc}
## Future directions {#disc-future}
## Conclusion {#disc-conclusion}

<!--ADS vs. CDS might not be right for kids who can learn from overhearing; Penny: ``clearly the relevant comparison is with speech not addressed to the child but to which the child is at least potentially attending. Speech around a non-attending child (e.g., speech on the telephone, or radio) is not likely to have any effects. Even if overheard speech is less effective in predicting later vocabulary size than speech addressed directly to the child, its role in Mayan lexical acquisition seems worth pursuing further'' (pp. 77; Brown 2014)-->

<!--Estimates of child-directed speech quantity may functionally predict children's word learning because they index the frequency with which children engage in rich, multimodal interactions with their caregivers; interactions in which children can actively and contingently elicit just the right linguistic information at just the right time to be optimally interesting and useful for learning (REFS; Eve's paper on homophonic Vs in French).-->

<!--One serious issue is how we define adult-like linguistic competence, especially within models in which we consider that adults still continue learning and that individual differences are rampant between adults in both linguistic knowledge and skill at every level, from phonetics to syntax to pragmatics, and of course vocabulary too. When we talk about language acquisition, especially cross-culturally, we have to be careful about what we think the ``target'' is and what are considered to be the developmental benchmarks children achieve. The focus recently has been on vocabulary acquisition, for some of the reasons outline above. However, vocabulary is a particularly literacy-centric view of language development. If we were to go back in time and set the seed of developmental language science in another culture, we might be much more concerned about the acquisition of kinship systems and other complex relational language, or in the ability to design elaborately indirect speech acts. Acquiring a language involves the mastery of a shockingly diverse array of skills and knowledge: not just linguistic symbols and systems, but also the infrastructure underlying their use (e.g., interactional skills), the cognitive-general skills supporting those systems. There's no reason _a priori_ to believe that every aspect of language acquisition is equally influenced by environmental input. For example, children's pointing frequency is influenced by the amount of pointing in their environment, but the age of pointing onset---the age which they first begin to point---appears unaffected by the frequency of pointing in their environment (REFS: Matthews, Liszkowski).-->

<!--means are meaningless if the thing that matters is some threshhold of interaction. well, not fully if we take evidence from cross-situational learning in wihch # of exposures matters, but even then we might expect bursty exposures to be more effective than non-bursty ones if memory is an issue... isn't there a Lew-Williams paper along these lines?-->

<!--Brown (2014) points out that other language- and culture-specific properties may facilitate word and language learning, including conversational repetition, specific verbs, and the centrality of gesture and gaze in learning the spatial system (pp. 77)-->

<!--Footnote: A lack of evidence linking input to grammatical outcomes may partly be due to practical limitations, e.g., there is no similarly convenient metric for syntactic development like the CDI (REFS??).-->

<!--Mayan work not yet mentioned:
de Leon, 1998??
Gaskins, 1990??
Gaskins, 1999??
Redfield & Villa Rojas, 1934??
Rogoff et al., 1993??
Lordes de Leon (2000): overhearing isn't just eavesdropping for Tsotsil kids because they're still socialized as participants-->


\newpage

# References {#refs}
<!--Brown, P. (2011). The cultural organization of attention. In Handbook of Language Socialization, A. Duranti, E. Ochs, and B.B. Schieffelin (eds.), 29-55. Blackwells.  
Brown, P. (2014). The interactional context of language learning in Tzeltal. In  I. Arnon, M. Casillas, C. Kurumada & B. Estigarribia (eds.) Language in Interaction: Studies in Honor of Eve V. Clark, 51–82. Amsterdam: John Benjamins.
Brown, P., and Gaskins, S. (2014). Language acquisition and language socialization. Handbook of Linguistic Anthropology, N. Enfield et al. (eds.),183-222. Cambridge: Cambridge University Press.-->

```{r create_r-references}
#r_refs(file = "r-references.bib")

```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
